\documentclass[letter,12pt]{article}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{array}
\usepackage{amssymb}
\usepackage{setspace}
%\usepackage[margin=1.5cm,vmargin={0pt,1cm},nohead]{geometry}
\usepackage[margin=1in,vmargin={1in,1in}]{geometry}
% Package that has the symbol for ``:=''
\usepackage{txfonts}
% Create fancy headers and footers for this document
\usepackage{fancyhdr}
%\usepackage{cite}
% The ``cite'' package causes the hyperlinks for the in-text references/citations to fail. I believe it is because this package overrides the default package for referencing. Hence, only use the ``cite'' package with the IEEE format.
% Package for ``turnstile'' binary relations, where letters are defined above and below symbols
\usepackage{turnstile}
\usepackage{extarrows}
% Package that provides the cross symbol
\usepackage{ifsym}
\usepackage{marvosym}
% Commands for using the package for hyperlinks - 
\usepackage[pdftex,
	pdftitle={Graphics and Color with LaTeX},
	pdfauthor={Patrick W Daly},
	pdfsubject={Importing images and use of color in LaTeX},
	pdfkeywords={LaTeX, graphics, color},
	pdfpagemode=UseOutlines,bookmarks, bookmarksopen,
	pdfstartview=FitH, colorlinks, linkcolor=blue, citecolor=blue, urlcolor=red,
]{hyperref}
\hypersetup{colorlinks, linkcolor=blue}
% Concatenate references
\usepackage{cite}
%\usepackage{/data/others/notes/clrscode3e}
\usepackage{/Applications/apps/comune/SienaLaTeX/rapporto/clrscode3e}

% definition of new \LaTeX command for the citation: \cite{Cimatti08} and \cite{Barrett09}
% This allows mathematical/logic symbols to be typeset with the font ``Zapf Chancery'' in ``\LaTeX\ math mode''. To typeset symbols in such font, try: \mathpzc{ABCdef123}
\DeclareMathAlphabet{\mathpzc}{OT1}{pzc}{m}{it}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Start of document
\begin{document}
\title{Resoures for Outreach Activities}
\date{\today}
\author{Zhiyang Ong
%\thanks{Email correspondence to: \href{mailto:ongz@acm.org}{ongz@acm.org}}
}
\maketitle

\begin{abstract} 
This is a list of resources for my outreach activities, which includes helping people explore careers in science, technology, engineering, and mathematics (STEM). It also includes resources to help parents and teachers of youths prepare youths for college; in addition, it has a list of scholarship resources. Furthermore, it has a list of resources that I use to help me with academic writing. Moreover, it also has resources to help people learn about various markets through publications based on market surveys of industries, such as semiconductors, biotechnology, and green technology. Finally, it has a list of resources to help people learn material from K-12 through advanced topics for graduate students.

\end{abstract}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Create the table of contents
\tableofcontents
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

{\tt This is last updated on September 8, 2010.}

\input{outreach}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Research Heuristics}
\label{researchheuristics}


The heuristic \proc{Find-Seminal-Papers} helps me find the seminal papers of an academic field, while the heuristic \proc{Keeping-Abreast-with-Researchers} helps me keep up with research trends (include determining emerging research trends and nascent research topics). \\

The references that I used for these heuristics are given as follows.\\
{\it Quora} [Online], ``How do I find the seminal papers of an academic field?''. Available online at: \url{http://www.quora.com/How-do-I-find-the-seminal-papers-of-an-academic-field}; last accessed on September 27, 2010. \\
{\it Quora} [Online], ``As a non-student, how do you keep up with interesting work in academia?''. Available online at: \url{http://www.quora.com/As-a-non-student-how-do-you-keep-up-with-interesting-work-in-academia}; last accessed on September 27, 2010. \\

Concerning \proc{Find-Seminal-Papers}, the sources of literature review include: \vspace{-0.3cm}
\begin{enumerate} \itemsep -4pt
\item journals
\item conference proceedings
\item Ph.D. theses
\item books
\item book chapters
\item technical reports
\item reading list of a reading group (or a seminar class in good graduate programs)
\item publication lists of researchers (preferably leading experts working in the field $\varphi$)
\item key publications of researchers who win achievement awards in the field $\varphi$: \vspace{-0.3cm}
	\begin{enumerate} \itemsep -2pt
	\item An example of this is the first conference paper on {\it Chaff} in {\it DAC 2001}.
	\end{enumerate}
\item repositories and digital libraries for good publications (e.g., {\it IEEE Xplore}, {\it ACM Digital Library}, {\it ScienceDirect}, {\it ProQuest Digital Dissertations}, {\it JSTOR} (short for Journal Storage), and {\it PubMed}), and domain-specific search engines (e.g., {\it Web of Science}, {\it Compendex}, {\it Scopus}, {\it Scirus}, {\it EMBASE}, and {\it Engineering Village})
\item generic scholarly search engines (e.g., Google Scholar)
\item academic social networking sites (e.g., Academia.edu)
\item reference lists of patents -- {\it Beware of patent infringement}
\end{enumerate}

Note that in some fields (e.g., social science), researchers publish foundational work in books, rather than in research/academic journals. As for the experts mentioned in line \ref{find-seminal-experts}, network and collaborate with these leading experts. The verification step in line \ref{find-seminal-verify} requires me to network with researchers in $\varphi$. While carrying out this verification process, ask these researchers for suggestions. For example, I can ask, ``What are the seminal publications/papers in $\varphi$?'' I note that carrying out this literature review is doing my homework before I seek help. If I approach others without doing my homework, it would be embarrassing if I don't understand what they are talking about; recall the brief conversation with Prof. Ofer Strichman (Technion) at {\it DAC 2009} about software verification and compiler validation. I am also aware that a high number of citations does not imply that a research paper is necessarily good. A significant, or considerable, proportion of the citations may be self-citations. Citations may refer to more recent publications, since not many people would read old publications. \\

Researchers who I can validate my list of seminal papers include: \vspace{-0.3cm}
\begin{enumerate} \itemsep -4pt
\item the list of researchers who I believe are the leading experts in $\varphi$
\item authors of my references
\item advanced Ph.D. students and postdocs: \vspace{-0.3cm}
	\begin{enumerate} \itemsep -2pt
	\item Good Ph.D. students and postdocs would have done a lot of literature research, and should know their research topic at least as well as their advisors.
	\end{enumerate}
\item editors of prestigious journals in $\varphi$
\item chairs of conferences and workshops (especially new/young workshops that are organized for nascent or fairly new research fields/topics)
\item keynote speakers at prestigious conferences
\item members of panel discussions at prestigious conferences
\item authors of famous textbooks in $\varphi$
\end{enumerate}



\begin{codebox}
\Procname{$\proc{Find-Seminal-Papers}(\varphi)$}
\zi	\Comment {\it Input $\varphi \gets $ research area that I am interested in}
\zi	\Comment {\it Output : seminal papers/publications in $\varphi$}
\li	\While I am still interested in $\varphi$
\li		\Do
		Perform a literature review on the research field $\varphi$.
\li		\While performing my literature review on $\varphi$
			\Do
\li			Determine which research publications are cited more frequently.
\li			Remember the authors who (co-)author the frequently cited research publications.
\li			Find out who the leading experts in $\varphi$ are, and look at their publications.	\label{find-seminal-experts}
\li			Verify my list of leading experts in $\varphi$ with researchers in $\varphi$.	\label{find-seminal-verify}
\zi
\zi			\Comment {\it Terminating Condition: When I have read more than enough papers/publications}
\zi			\Comment {\it (e.g., 50-200 journal/conference papers).}
\li			\End
\li		Take advantage of folksonomy, and use the tags of {\it arXiv} and {\it Mendeley}
\zi		(and perhaps, {\it CiteULike}) to locate new/recent submissions in $\varphi$.
\li		Use {\it Google Scholar} to help me keep track of the number of citations
\zi		for a given research publication.
\zi		\End
\end{codebox}

{\color{blue} A general rule for using \proc{Keeping-Abreast-with-Researchers} is that the selected conference or journal papers shall be well-written.} If the paper is difficult to read (as in poorly written), it is hard to follow the rest of their work. Also, just because a paper is technically complicated, it does not mean that it is a good paper. Concerning line \ref{keeping-abreast-pub-list} of \proc{Keeping-Abreast-with-Researchers}, I can take advantage of resources such as the web pages of researchers and research groups/labs, {\it DBLP}, {\it IEEE Xplore}, and {\it ACM Digital Library}. To find out about recently published books (see line \ref{keeping-abreast-books}), look at the collection of books in bookstores that sell academic books (course textbooks and scholarly books). In particular, check out the student bookstores of good colleges and universities, as well as the pamphlets of academic publishers, such as {\it John Wiley {\rm \&} Sons} (or {\it Wiley}), {\it Morgan Kaufmann Publishers}, {\it Springer Science+Business Media} (or {\it Springer}), {\it Elsevier}, and {\it IOS Press}. In addition, look at the collections of university presses, such as {\it MIT Press}, {\it Cambridge University Press}, and {\it Oxford University Press}. Elaborating on line \ref{keeping-abreast-follow-conf}, make a shortlist of 5-10 conference papers from the advanced program of conferences (which includes a list of accepted papers), and email the authors for copies of their papers. After each major conference, ask friends who have attended that conference to discuss their top 3-5 presentations. Subsequently, read the corresponding conference papers for these presentations.

\begin{codebox}
\Procname{$\proc{Keeping-Abreast-with-Researchers}(\beta)$}
\li	\Comment {\it Input: $\beta \gets $ research area that I am interested in}
\li	\Comment {\it Output: conference papers, journal papers, {\rm \&} patents, }
\li	\While I am interested in $\beta$
		\Do
\li		Keep track of the publication record of researchers.		\label{keeping-abreast-pub-list}
\li		Take advantage of folksonomy, and use the tags of {\it arXiv} and {\it Mendeley}.
\zi		(and perhaps, {\it CiteULike}) to locate new/recent submissions in $\beta$.
\li		For each publication, determine its key references and look them up.
\zi		\Comment {\it That is, form the directed graph of research publications in $\beta$.}
\zi		\Comment {\it This will lead me to other interesting papers and new researchers to keep track of.}
\li		Find recent books that interest me, and look up their primary references/citations on
\zi		the best techniques/methodologies (or recent techniques/methodologies).	\label{keeping-abreast-books}
\li		Keep track of the specialists in $\beta$ and the relevant topics on {\it Quora} and {\it Facebook}.
\li		Ask open-ended questions on {\it Quora} and {\it Facebook}, which specialists may answer.
\li		Information about nascent or fairly new research fields/topics may emerge on {\it Facebook}.
\zi		\Comment {\it Information about new/recent tools and computer languages}
\zi		\Comment {\it may also emerge on {\it Facebook} and blogs (and perhaps {\it Wikipedia}).}
\li		Follow the major conferences in $\beta$ casually.		\label{keeping-abreast-follow-conf}
\li		Attend academic talks whenever possible, especially at good research universities.
\zi		\Comment {\it High-tech companies with research labs have their own academic talks,}
\zi		\Comment {\it which are closed to public.}
\li		Spend at least 1 day per month digging deep into the archive, \& recursively follow the citations.
\li		Be familiar with the rough work of superstars in $\beta$.
\li		Follow the work of good research labs in $\beta$.
\li		Pay attention to keynote speeches and panel discussions at major conferences.
\li		Look at the roadmaps for $\beta$ (if any), which present challenges to be tackled
\zi		under long-term research (8-15 years).
\li		Check out workshops for nascent or fairly new research fields/topics.
\li		Look at handbooks, which provide a wealth of information on an academic field or research topic.
\li		Look at the {\it Future Work} sections of Ph.D. theses in $\beta$.
\zi		\Comment {\it Especially if they win some sort of dissertation award (e.g., that from ACM).}
\li		Check out ``generic'' journal publications that have good survey papers.
\zi		\Comment {\it E.g., ``Proceedings of the IEEE'' or ``Journal of the ACM''.}
\li		Look at the web pages of government agencies and professional organizations,
\zi		which may include roadmaps.
\li		Look at the publication lists (and job advertisements) of start-ups (if any).
\li		Ask researchers in $\beta$ what are they reading.
\li		Look for highly-rated books in $\beta$, and go through the sorted list (based on year of publication).
\li		Keep track of good blogs written by good researchers (i.e., academic blogs)
\zi		and industry analysts via RSS feeds.
\zi		\End
\end{codebox}




%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Research Resources}
\label{researchresources}

Resources for research, and educational and learning material: \vspace{-0.3cm}
\begin{enumerate} \itemsep -4pt
\item International Technology Roadmap for Semiconductors (ITRS): \url{http://public.itrs.net/}
\item CATRENE (Cluster for Application and Technology Research in Europe on NanoElectronics): \url{http://www.catrene.org/index.php}
\item Social networking sites: \vspace{-0.3cm}
	\begin{enumerate} \itemsep -2pt
	\item For academics, see \url{http://www.academia.edu/}
	\item ResearchGATE Corporation: \url{http://www.researchgate.net/}
	\item MyNetResearch: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item Features: \url{http://www.mynetresearch.com/Features.aspx}
		\item Resources: \url{http://www.mynetresearch.com/ResearcherLinks.aspx}
		\item Can facilitate project management, and provides public and private file sharing
		\item \url{http://www.mynetresearch.com/}
		\end{enumerate}
	\item {\it weSRCH.com}: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item ``For professionals who engage in the fields of High Tech, Green Tech, and Medicine''
		\item It has an online forum, and is a resource for news in the high tech, green tech, and bio tech industries.
		\item \url{http://www.wesrch.com/}
		\end{enumerate}
	\end{enumerate}
\item Educational resources and ``open-source'' textbooks: \vspace{-0.3cm}
	\begin{itemize} \itemsep -2pt
	\item OpenCourseWare Consortium: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item \url{http://www.ocwconsortium.org/}
		\item OCW Finder: \url{http://www.ocwfinder.org/}
		\item MIT OpenCourseWare: \url{http://ocw.mit.edu/index.htm}
		\end{enumerate}
	\item Connexions: \url{http://cnx.org/}
	\item Nature Publishing Group (a division of Macmillan Publishers Limited): \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item {\it Scitable} is a free science library and personal learning tool brought to you by Nature Publishing Group, the world's leading publisher of science. Available online at: \url{http://www.nature.com/scitable}; last accessed on January 1, 2010.: \vspace{-0.1cm}
			\begin{enumerate} \itemsep -1pt
			\item {\it eBooks}. Nature Education e-books are intuitive introductions to a range of topics relevant to science students, young scientists, and science enthusiasts of all ages. Available online at: \url{http://www.nature.com/scitable/topics}; last accessed on January 1, 2010.
			\end{enumerate}
		\end{enumerate}
	\item {\it Quora}, which is a collection of questions and answers: \url{http://www.quora.com/}
	\item {\it SelfSolved} is a personal and social information repository for people who solve problems: \url{http://selfsolved.com/}
	\item Flat World Knowledge: \url{http://www.flatworldknowledge.com/}
	\item Liquid Publications (LiquidPub): \url{http://project.liquidpub.org/}
	\item OER Commons: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item A project of the Institute for the Study of Knowledge Management in Education, ISKME
		\item \url{http://www.oercommons.org/}
		\end{enumerate}
	\item NIXTY: \url{http://nixty.com/}
	\item Learning Is For Everyone: \url{http://www.learningis4everyone.org/}
	\item BCcampus OER Portal: \url{http://freelearning.ca/about/}
	\item iBerry: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item \url{http://iberry.com/}
		\item \url{http://iberry.com/cms/} and \url{http://iberry.com/cms/OCW.htm}
		\end{enumerate}
	\item InTech: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item \url{http://www.intechweb.org/}
		\item \url{http://www.intechopen.com/}
		\end{enumerate}
	\item Open Educational Resources (OER): \url{http://wiki.creativecommons.org/OER}
	\item Open Learning Initiative: \url{http://oli.web.cmu.edu/openlearning/}
	\item Peer 2 Peer University (P2PU): \url{http://www.p2pu.org/}
	\item Curtis J. Bonk, Book Resources [ for ] ``The World Is Open: How Web Technology Is Revolutionizing Education,'' Jossey-Bass (a Wiley imprint), San Francisco, CA. Available at: \url{http://worldisopen.com/resources.php}; last accessed on September 4, 2010.
	\item Wikiversity (from the Wikimedia Foundation): \url{http://en.wikiversity.org/wiki/Wikiversity:Main_Page}
	\item Einztein Knowledge Network: \url{http://www.einztein.com/}
	\item Saylor Foundation: \url{http://www.saylor.org/}
	\item Knewton: \url{http://www.knewton.com/}
	\item wePapers: \url{http://www.wepapers.com/}
	\item CourseSmart: \url{http://www.coursesmart.com/}
	\item WikiEducator: \url{http://wikieducator.org/Main_Page}
	\item Community College Consortium for Open Educational Resources: \url{http://oerconsortium.org/}
	\item Online encyclopedia: \url{http://openresearch.org/wiki/Main_Page}
	\item Google: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item Google ebookstore (Google eBooks): \url{http://books.google.com/ebooks}
		\item Google Books Ngram Viewer: \vspace{-0.1cm}
			\begin{enumerate} \itemsep -1pt
			\item \url{http://ngrams.googlelabs.com/}
			\item Datasets: \url{http://ngrams.googlelabs.com/datasets}
			\end{enumerate}
		\end{enumerate}
	\item {\bf \color{blue} The Assayer} (has textbooks in many topics): \url{http://theassayer.org/}
	\item {\bf \color{blue} Culturomics} Resources: \url{http://www.culturomics.org/Resources/links}
	\item The Dana Foundation: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item \url{http://www.dana.org/news/publications/}
		\item Literature review on brain research that is updated annually
		\end{enumerate}
	\item Cramster: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item \url{http://www.cramster.com/}
		\item Offers help in electrical engineering and computer science, among other subjects (e.g., writing, mathematics, and physics)
		\end{enumerate}
	\item University of Southern California: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item Material for classes (mostly in engineering): \url{http://www-classes.usc.edu/}
		\item USC Andrew and Erna Viterbi School of Engineering: \vspace{-0.1cm}
			\begin{enumerate} \itemsep -1pt
			\item \url{http://www-classes.usc.edu/engr/}
			\item Ming Hsieh Department of Electrical Engineering: \url{http://www-classes.usc.edu/engr/ee-s/}
			\end{enumerate}
		\end{enumerate}
	\item University of Washington: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item Department of Mathematics: \vspace{-0.1cm}
			\begin{enumerate} \itemsep -1pt
			\item List of open source projects in symbolic and numerical computing, and {\bf online computer science and mathematics books} (by Minh Van Nguyen): \url{http://sage.math.washington.edu/home/mvngu/misc.html}
			\end{enumerate}
		\end{enumerate}
	\item Princeton University: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item UChannel (University Channel): Contains ``videos of academic lectures and events'', \url{http://uc.princeton.edu/main/}; \url{http://uc.princeton.edu/main/index.php/about-us-mainmenu-2}; or \url{http://uc.princeton.edu/main/index.php/home-mainmenu-1}
		\item Office of Information Technology: \vspace{-0.1cm}
			\begin{enumerate} \itemsep -1pt
			\item Event Streaming WebMedia: Source of academic lectures, \url{http://hulk03.princeton.edu:8080/WebMedia/lectures/}
			\end{enumerate}
		\item Educational Technologies Center: Almagest, \url{http://etcweb.princeton.edu/almagest3/}
		\end{enumerate}
	\item Virginia Tech (Virginia Polytechnic Institute and State University): \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item Department of Computer Science: \vspace{-0.1cm}
			\begin{enumerate} \itemsep -1pt
			\item Graduate classes: \url{http://www.cs.vt.edu/graduate/courses}
			\item Undergraduate classes: \url{http://www.cs.vt.edu/undergraduate/courses}
			\item List of all classes: \url{http://ei.cs.vt.edu/courses.html}
			\end{enumerate}
		\end{enumerate}
	\item University of Adelaide: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item eBooks@Adelaide: \vspace{-0.1cm}
			\begin{enumerate} \itemsep -1pt
			\item Classic Works of Literature, Philosophy, Science, History, and Exploration and Travel: \url{http://ebooks.adelaide.edu.au/}
			\end{enumerate}
		\end{enumerate}
	\item Colorado School of Mines: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item Department of Physics: \vspace{-0.1cm}
			\begin{enumerate} \itemsep -1pt
			\item Samizdat Press, \url{http://samizdat.mines.edu/}, contains books in: \vspace{-0.1cm}
				\begin{itemize} \itemsep -1pt
				\item Linear Algebra and Multidimensional Geometry 
				\item Differential Geometry
				\item Tensor Analysis
				\item Classical Electrodynamics and the Theory of Relativity
				\item Continuum Mechanics 
				\item Genetic Algorithms
				\item Geomechanics
				\item Greek Seismology
				\item Geophysical Inverse Theory 
				\item Geophysics
				\item finite element analysis
				\item Inverse Problem Theory 
				\end{itemize}
			\end{enumerate}
		\end{enumerate}
	\item IEEE: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item IEEE eLearning Library: \url{http://ieee-elearning.org/}
		\item IEEE Career Resources: \url{http://ieee.org/education_careers/careers/index.html}
		\item IEEE Online Professional Development: \url{http://ieee.org/education_careers/education/prodev/index.html}
		\item IEEE Computer Society: \vspace{-0.1cm}
			\begin{enumerate} \itemsep -1pt
			\item e-learning campus: \url{http://www.computer.org/portal/web/e-learning/home}
			\end{enumerate}
		\end{enumerate}
	\item ACM: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item ACM Tech Pack: \url{http://techpack.acm.org/}
		\item ACM Learning Center (has online books): \url{http://learning.acm.org/}
		\end{enumerate}
	\item IBM: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item Program Analysis Group; IBM T.J. Watson Research Center: \vspace{-0.1cm}
			\begin{enumerate} \itemsep -1pt
			\item Eran Yahav, {\it misc}, IBM. Available online at: \url{http://www.research.ibm.com/people/e/eyahav/misc.html}; last accessed on September 28, 2010. [ Also has resources about learning German and how to play the guitar. ]
			\end{enumerate}
		\end{enumerate}
	\item U.S. National Academies: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item National Academies Press: \url{http://www.nap.edu/}
		\item Proceedings of the National Academy of Sciences: \url{http://www.pnas.org/}
		\item Publications: \url{http://www.nationalacademies.org/publications/}
		\end{enumerate}
	\item The National Science Foundation: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item {\it Science and Engineering Statistics: Publications, data, and analyses about the nation's science and engineering resources}, Division of Science Resources Statistics (SRS). Available online at: \url{http://www.nsf.gov/statistics/}; last accessed on September 25, 2010.
		\item {\it Science and Engineering Indicators: 201X}, Division of Science Resources Statistics, National Science Foundation, Arlington, VA, January 2010. Available online at: \url{http://www.nsf.gov/statistics/indicators/}; last accessed on September 25, 2010. [ The 2010 issue is available at: \url{http://www.nsf.gov/statistics/seind10/}. ]
		\end{enumerate}
	\item Ewing Marion Kauffman Foundation: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item Links: \url{http://sciencecommons.org/resources/links/}
		\end{enumerate}
	\item Open Culture: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item \url{http://www.openculture.com/}
		\item ``free cultural \& educational media on the web''
		\end{enumerate}
	\item R\&D Magazine (from Advantage Business Media): \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item \url{http://www.rdmag.com/}
		\item R\&D 100 Awards 201X: \url{http://www.rdmag.com/Awards/RD-100-Awards/R-D-100-Awards/}
		\end{enumerate}
	\item The Academy of American Poets: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item \url{http://www.poets.org/index.php}
		\item ``The Road Not Taken,'' by Robert Frost. Available online at: \url{http://www.poets.org/viewmedia.php/prmMID/15717}; last accessed on September 28, 2010.
		\end{enumerate}
	\item William Stallings: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item Xentrik: \vspace{-0.1cm}
			\begin{enumerate} \itemsep -1pt
			\item Tutorial for creating and maintaining web pages: \url{http://www.xentrik.net/}
			\end{enumerate}
		\item Resources for CS students: \vspace{-0.1cm}
			\begin{enumerate} \itemsep -1pt
			\item {\it Computer Science Student Resource Site}, \url{http://www.computersciencestudent.com/}
			\item {\it Computer Science Student Resource Site: How-To}, \url{http://www.computersciencestudent.com/SS/SS-howto.html}
			\item {\it Computer Science Student Resource Site: Computer Science Careers}, \url{http://www.computersciencestudent.com/SS/SS-career.html}
			\end{enumerate}
		\end{enumerate}
	\end{itemize}
\item Videos of lectures, research talks/presentations, and seminars: \vspace{-0.3cm}
	\begin{enumerate} \itemsep -2pt
	\item {\it iTunes U}: \url{http://www.apple.com/education/itunes-u/}
	\item {\it YouTube}: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item \url{http://www.youtube.com/}
		\item YouTube EDU: \url{http://www.youtube.com/education?b=400}
		\end{enumerate}
	\item \url{http://videolectures.net/}
	\item Academic Earth: \url{http://www.academicearth.org/}
	\item MyNetResearch Videos: \url{http://videos.mynetresearch.com/Default.aspx}
	\item Computer Science: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item University of Illinois at Urbana-Champaign (UIUC): \vspace{-0.1cm}
			\begin{enumerate} \itemsep -1pt
			\item College of Engineering; Department of Computer Science: \url{http://cs.illinois.edu/lectures}
			\end{enumerate}
		\end{enumerate}
	\item Mathematics: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item Institute for Mathematics and its Applications (IMA) at the University of Minnesota, Twin Cities: \url{http://www.ima.umn.edu/videos/}
		\end{enumerate}
	\end{enumerate}
\item Xuropa: \vspace{-0.3cm}
	\begin{enumerate} \itemsep -2pt
	\item the electronic design online community; the {\tt Facebook} for people working in EDA, IP design/verification/services, (rest of the) semiconductor industry (including design, CAD, verification, test, and device engineers), software industry, and systems people (including those in embedded systems, automobile industry, and medical systems)
	\item see \url{http://xuropa.com/}
	\end{enumerate}
\end{enumerate}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Resources for Market Research as well as Social, Economic, and Political Issues}
\label{resourcesmktresearch}

Resources for market research as well as social, economic, and political issues: \vspace{-0.3cm}
\begin{enumerate} \itemsep -4pt
\item Gary Smith EDA (GSEDA): \url{http://www.garysmitheda.com/}
\item VLSI Research Inc: \url{https://www.vlsiresearch.com/}
\item Future Horizons: \url{http://www.futurehorizons.com/}
\item Gartner [or Gartner Dataquest]: \url{http://www.gartner.com/technology/home.jsp}
\item iSuppli Corporation: \url{http://www.isuppli.com/Pages/Home.aspx}
\item Linley Group: \vspace{-0.3cm}
	\begin{enumerate} \itemsep -2pt
	\item {\it Processor Watch}, ``a free electronic newsletter on high-performance microprocessors'': \url{http://www.mdronline.com/processor_watch/}
	\item \url{http://www.linleygroup.com/}
	\end{enumerate}
\item Semico Research Corp: \url{http://www.semico.com/}
\item Other organizations/companies that provide forecasts for the semiconductor market: \vspace{-0.3cm}
	\begin{enumerate} \itemsep -2pt
	\item Semiconductor Intelligence: \url{http://www.semiconductorintelligence.com/}
	\item Semiconductor Industry Capacity Statistics (SICAS): \url{http://www.sicas.info/}
	\item Semiconductor Equipment and Materials International (SEMI\textregistered): \url{http://www.semi.org/en/index.htm}
	\item WSTS (World Semiconductor Trade Statistics): \url{http://www.wsts.org/}
	\item Semiconductor Industry Association (SIA): \url{http://www.sia-online.org/}
	\item International Data Corporation (IDC): \url{http://www.idc.com/}
	\item IC Insights: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item {\it The McClean Report: A Complete Analysis and Forecast of the Integrated Circuit Industry}: \url{http://www.icinsights.com/prodsrvs/mcclean/mcclean.html}
		\item {\it IC Market Drivers: A Study of Emerging and Major End-Use Applications Fueling Demand for Integrated Circuits} helps identify opportunities for growth and evaluates the potential for new applications that are expected to fuel the market for integrated circuits through 2013. See \url{http://www.icinsights.com/prodsrvs/marketdrivers/marketdrivers.html}.
		\item {\it O$\cdot$S$\cdot$D Report: A Market Analysis and Forecast for Optoelectronics, Sensors, and Discretes} provides information about the end-use application, regional market analysis, leading supplier rankings, device history, and technology trends for: \vspace{-0.2cm}
			\begin{itemize} \itemsep -2pt
			\item optoelectronics: \vspace{-0.1cm}
				\begin{itemize} \itemsep -1pt
				\item CCD and CMOS Image Sensors
				\item Laser Transmitters and Pick-Ups (for fiber-optic networks)
				\item Solid-State Lamps and LEDs
				\item Infrared Devices
				\item Couplers, Isolators
				\item Optical Switches
				\item Digital Character Displays
				\end{itemize}
			\item sensors/actuators (including MEMS-based): \vspace{-0.1cm}
				\begin{itemize} \itemsep -1pt
				\item Pressure Sensors
				\item Acceleration and Yaw Sensors
				\item Magnetic-Field Sensors
				\item Temperature Sensors
				\item Fingerprint ID Chips
				\item Actuators
				\end{itemize}
			\item discretes: \vspace{-0.1cm}
				\begin{itemize} \itemsep -1pt
				\item Power Transistors and Modules (IGBTs, power IGBTs, and power FETs)
				\item Small-Signal Transistors
				\item Switching Transistors
				\item Diodes, Rectifiers, and Thyristors
				\item RF/Microwave Transistors and Modules
				\end{itemize}
			\end{itemize}
		\item \url{http://www.icinsights.com/prodsrvs/osdreport/osdreport.html}
		\item {\it MEMS 2010: A Realistic Look Beyond the Hype} (Special Study). See \url{http://www.icinsights.com/prodsrvs/specialstudies/mems/mems.html}.
		\item {\it Global Wafer Capacity Analysis and Forecast} (Special Study). See \url{http://www.icinsights.com/prodsrvs/specialstudies/globalcapacity/globalcapacity.html}.
		\item {\it Strategic Reviews Online} offers quick access to thorough examinations of companies involved in the design and manufacture of integrated circuits. Whether a supplier owns a fab or is fabless, has sales of several million or several billion dollars,  {\it Strategic Reviews Online} provides detailed reviews of the operations and activities of more than 200 of the world's established and emerging IC companies (totaling about 770 printed pages worth of valuable information). Access {\it Strategic Reviews Online: Extensive Profiles of the World's IC Manufacturers and Fabless Suppliers} @ \url{http://www.icinsights.com/prodsrvs/reviews/reviews.html}.
		\item \url{http://www.icinsights.com/}
		\end{enumerate}
	\item ABI Research: \url{http://www.abiresearch.com/home.jsp}
	\item HTE Research, Inc.: \url{http://www.hteresearch.com/}; also see {\it InsideChips} @ \url{http://www.insidechips.com/}
	\item In-Stat, LLC: \url{http://www.instat.com/}
	\item Chipworks: \url{http://www.ice-corp.com/}
	\end{enumerate}
\item Yole D{\'{e}}veloppement: \url{http://www.yole.fr/}
\item Lux Research (solar, nanomaterials, alternative power, water, biosciences): \url{http://www.luxresearchinc.com/}
\item Pike Research (global clean technology markets: smart energy, clean transportation, clean industry, and building efficiency): \url{http://www.pikeresearch.com/}
\item Deloitte Consulting: \vspace{-0.3cm}
	\begin{enumerate} \itemsep -2pt
	\item see market survey of industries @ \url{http://www.deloitte.com/view/en_US/us/industries/index.htm}
	\item \url{http://www.deloitte.com/view/en_US/us/Insights/centers/index.htm}
	\item see Deloitte Review @ \url{http://www.deloitte.com/view/en_US/us/Insights/Browse-by-Content-Type/deloitte-review/index.htm}
	\item see Deloitte Research @ \url{http://www.deloitte.com/view/en_US/us/Insights/Browse-by-Content-Type/research/index.htm}
	\item see Case Studies @ \url{http://www.deloitte.com/view/en_US/us/Insights/Browse-by-Content-Type/Case-Studies/index.htm}
	\item see Deloitte Technology Services Consulting @ \url{http://www.deloitte.com/view/en_US/us/Services/consulting/technology-consulting/index.htm}
	\item see Deloitte Debates @ \url{http://www.deloitte.com/view/en_US/us/Insights/Browse-by-Content-Type/deloitte-debates/index.htm}
	\end{enumerate}
\item Morgan Stanley: \vspace{-0.3cm}
	\begin{enumerate} \itemsep -2pt
	\item Technology Research: \url{http://www.morganstanley.com/institutional/techresearch/}.
	\item Journal of Applied Corporate Finance: \url{http://www.morganstanley.com/views/jacf/index.html}.
	\item Perspectives: \url{http://www.morganstanley.com/views/perspectives/index.html}.
	\item Global Strategy Roundup: \url{http://www.morganstanley.com/views/gsr/index.html}.
	\item Global Economic Forum: \url{http://www.morganstanley.com/views/gef/index.html}.
	\end{enumerate}
\item McKinsey \& Company: See McKinsey Quarterly @ \url{http://www.mckinseyquarterly.com/home.aspx?srid=6} and McKinsey Global Institute (MGI) @ \url{http://www.mckinsey.com/mgi/}
\item Accenture Research \& Insights: \url{http://accenture.ie/global/research_and_insights/research_and_insights_int}; also, see \url{http://accenture.ie/Global/Services/By_Industry/Electronics_and_High_Tech/Services/ServicesSemiconductorInd.htm} for Accenture's Semiconductor Business
\item Ernst \& Young: \url{http://www.ey.com/SG/en/Industries}
\item Boston Consulting Group (BCG): \vspace{-0.3cm}
	\begin{enumerate} \itemsep -2pt
	\item \url{http://www.bcg.com/expertise_impact/publications/default.aspx}
	\item Industries that BCG provides services for and analysis of: \url{http://www.bcg.com/expertise_impact/industries/default.aspx}
	\item BCG Strategy Institute: \url{http://www.bcg.com/about_bcg/strategyinstitute/default.aspx} and \url{http://www.bcg.com/about_bcg/strategyinstitute/research/default.aspx}.
	\end{enumerate}
\item PricewaterhouseCoopers: \vspace{-0.3cm}
	\begin{enumerate} \itemsep -2pt
	\item Industry sectors: \url{http://www.pwc.com/gx/en/industry-sectors/index.jhtml}
	\item Research \& insights: \url{http://www.pwc.com/gx/en/research-insights/index.jhtml}
	\end{enumerate}
\item Pew Research Center, \url{http://pewresearch.org/}: \vspace{-0.3cm}
	\begin{enumerate} \itemsep -2pt
	\item Pew Global Attitudes Project: \url{http://pewglobal.org/}
	\item Pew Internet and American Life Project: \url{http://www.pewinternet.org/}
	\item Pew Social and Demographic Trends Project: \url{http://pewsocialtrends.org/}
	\item Pew Forum on Religion and Public Life: \url{http://pewforum.org/}
	\item Pew Research Center for the People and the Press: \url{http://people-press.org/}
	\item Project for Excellence in Journalism: \url{http://pewsocialtrends.org/}
	\item Pew Hispanic Center: \url{http://pewhispanic.org/}
	\end{enumerate}
\item Brookings Institution: \url{http://www.brookings.edu/}
\item Knowledge@Wharton from University of Pennsylvania's Wharton School [of business]: \url{http://knowledge.wharton.upenn.edu/}
\item Goldman Sachs: See Global Markets Institute @ \url{http://www2.goldmansachs.com/ideas/global-markets-institute/index.html}
\item Capgemini: \vspace{-0.3cm}
	\begin{enumerate} \itemsep -2pt
	\item Publishes a ``World Retail Banking Report 20XY''; see \url{http://www.capgemini.com/insights-and-resources/by-publication/world_retail_banking_report_2009/}
	\item Insights \& Resources: Publications; see \url{http://www.capgemini.com/insights-and-resources/by-publication/}
	\end{enumerate}
\item Carnegie Corporation of New York: \vspace{-0.3cm}
	\begin{enumerate} \itemsep -2pt
	\item Publications (including magazines, reports, and books): \url{http://carnegie.org/publications/}
	\end{enumerate}
\item {\it Demos}: Publications, \url{http://www.demos.org/publication_list.cfm}
\item Manhattan Institute for Policy Research: \url{http://www.manhattan-institute.org/tools/bytopic.php}
\item Ford Foundation: Library, \url{http://www.fordfoundation.org/library}
\item The Foundation Center: \url{http://foundationcenter.org/gainknowledge/}
\item Working Group on Extreme Inequality: Resources, \url{http://extremeinequality.org/?page_id=4}
\item The Rockefeller Foundation: \url{http://www.rockefellerfoundation.org/news/publications}
\item Emergent Research: \vspace{-0.3cm}
	\begin{enumerate} \itemsep -2pt
	\item \url{http://www.emergentresearch.com/}
	\item Has research reports about entrepreneurship, and the types of entrepreneurship.
	\end{enumerate}
\end{enumerate}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Resources for Research Publications}
\label{researchpubsresources}


Resources for research publications: \vspace{-0.3cm}
\begin{enumerate} \itemsep -4pt
\item {\it Google Scholar}: \url{http://scholar.google.com/}
\item {\it CiteSeer$^{\rm x}$}: \vspace{-0.3cm}
	\begin{enumerate} \itemsep -2pt
	\item \url{http://citeseerx.ist.psu.edu/}
	\item Scientific Literature Digital Library and Search Engine
	\end{enumerate}
\item {\it arXiv}: \vspace{-0.3cm}
	\begin{enumerate} \itemsep -2pt
	\item Open access to 624,659 e-prints in Physics, Mathematics, Computer Science, Quantitative Biology, Quantitative Finance and Statistics
	\item \url{http://arxiv.org/}
	\end{enumerate}
\item Microsoft Academic Search: \url{http://academic.research.microsoft.com/}
\item Scitopia: \url{http://www.scitopia.org/scitopia/}
\item Scirus: \url{http://www.scirus.com/}
\item Scopus: \url{http://www.scopus.com/home.url}
\item SciVerse Scopus: \url{}
\item {\it eScholarship}, California Digital Library and The Berkeley Electronic Press: \vspace{-0.3cm}
	\begin{enumerate} \itemsep -2pt
	\item \url{http://www.escholarship.org/}
	\item eScholarship provides a suite of open access, scholarly publishing services and research tools that enable departments, research units, publishing programs, and individual scholars associated with the University of California to have direct control over the creation and dissemination of the full range of their scholarship.
	\item With eScholarship, you can publish the following original scholarly works on a dynamic research platform available to scholars worldwide: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item Journals
		\item Books
		\item Working Papers
		\item Conference Proceedings
		\item Seminar/Paper Series
		\end{enumerate}
	\end{enumerate}
\item MyNetResearch's Global Directory of Doctoral Dissertations: \url{http://www.mynetresearch.com/Wiki/Default.aspx}
\item Social Science Research Network (SSRN): \url{http://ssrn.com/}
\item Universitat Polit{\`{e}}cnica de Catalunya: \vspace{-0.3cm}
	\begin{enumerate} \itemsep -2pt
	\item Department of Computer Languages and Systems (Departament de Llenguatges i Sistemes Inform{\`{a}}tics, LSI): \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item LSI Tech Reports archive: \url{http://www.lsi.upc.edu/dept/techreps/techreps.html}
		\end{enumerate}
	\end{enumerate}
\end{enumerate}





Selected research publications: \vspace{-0.3cm}
\begin{enumerate} \itemsep -4pt
\item {\it Ubiquity}: \vspace{-0.3cm}
	\begin{enumerate} \itemsep -2pt
	\item \url{http://ubiquity.acm.org/}
	\item ``A peer-reviewed, online publication of ACM dedicated to the future of computing and the people who are creating it.''
	\end{enumerate}
\end{enumerate}








%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Resources on Technical Writing}
\label{technicalwritingresources}

Resources for academic/technical writing: \vspace{-0.3cm}
\begin{itemize} \itemsep -4pt
\item Individuals: \vspace{-0.3cm}
	\begin{enumerate} \itemsep -2pt
	\item Kenneth M. Hanson (Los Alamos National Laboratory): \url{http://kmh-lanl.hansonhub.com/techwriting.html} or \url{http://public.lanl.gov/kmh/techwriting.html}
	\item William Stallings, ``Writing Guide''. Available at: \url{http://www.williamstallings.com/Extras/Writing_Guide.html}; last accessed on August 25, 2010.
	\item Lorraine Lica, ``The Distinction Between WHICH and THAT With Diagrams: Especially for Scientists''. Available at: \url{http://home.earthlink.net/~llica/wichthat.htm}; last accessed on September 3, 2010.
	\item Michael Nielsen, {\it Six Rules for Rewriting}, posted on his blog on August 19, 2008. Available online at: \url{http://michaelnielsen.org/blog/six-rules-for-rewriting/}; last accessed on December 26, 2010.
	\end{enumerate}
\item ACM: \vspace{-0.3cm}
	\begin{enumerate} \itemsep -2pt
	\item ACM SIG Proceedings: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item Gerry Murray, ``Conference Proceedings \LaTeXe\ Submission FAQ,'' Association for Computing Machinery, March 10, 2010. Available at: \url{http://www.acm.org/sigs/publications/sigfaq}; last accessed on September 14, 2010.
		\end{enumerate}
	\end{enumerate}
\item IEEE: \vspace{-0.3cm}
	\begin{enumerate} \itemsep -2pt
	\item {\it A Plagiarism FAQ}, IEEE Intellectual Property Rights, Piscataway, NJ. Available online at: \url{http://portal.ieee.org/web/publications/rights/plagiarism_FAQ.html}; last accessed on September 25, 2010.
	\item {\it IEEE Intellectual Property Rights}, IEEE Intellectual Property Rights, Piscataway, NJ. Available online at: \url{http://portal.ieee.org/web/publications/rights/index.html}; last accessed on September 25, 2010.
	\item IEEE Solid-State Circuits Society: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item Jan Van der Spiegel and Kenneth C. Smith, ``Tools: ISSCC Paper Submissions - Increasing the Likelihood of Success (Tips on Increasing Your Chance of ISSCC Acceptance).'' Available online at: \url{http://www.ieee.org/portal/site/sscs/menuitem.f07ee9e3b2a01d06bb9305765bac26c8/index.jsp?&pName=sscs_level1_article&TheCat=2010&path=sscs/07Summer&file=Tools.xml}; last accessed on September 18, 2010 \cite{VanderSpiegel2007}. [ ``How to Write a Paper for ISSCC'' is available as a flash presentation, prepared for students at A-SSCC in November, 2006, at \url{http://sscs.org/Chapters/07ChptLnch/07FEBCafe.htm}. Alternative reference for this set of presentation slides: Jan Van der Spiegel and Kenneth C. Smith, ``Writing a good ISSCC paper: Tips on how to increase the chances of paper acceptance,'' presentation at the IEEE Asian Solid-State Circuits Conference 2006, November, 2006. Available online at: \url{http://isscc.org/doc/2008/WritingISSCCpaperJVdS_Nov06b.ppt}; last accessed on December 28, 2010. ]. \vspace{-0.1cm}
			\begin{enumerate} \itemsep -1pt
			\item Before I commence writing the paper, ask myself the following questions: \vspace{-0.1cm}
				\begin{itemize} \itemsep -1pt
				\item What results do I want to communicate?
				\item How does my work improve on previously published work?
				\item Who are the key players in this area?
				\item What are the latest references?
				\end{itemize}
			\item Know the latest key references related to your work
			\item Do not use old references, except to emphasize the time scale of the problem.
			\item The use of good references tells the reviewers that you are aware of the latest developments in the field.
			\item Refer to all references in the text of the paper, and comment briefly on each.
			\item Do not refer to only your own work.
			\item Start writing the paper with the Conclusions section. This forces you to think about what you want to say.
			\item Be quantitative in the Conclusions: Summarize the important measured results, give numerical data; and relate them to earlier work.
			\item Once the conclusions are written, backfill the paper.
			\item Be explicit and concrete: Quantify the results.
			\item Put your results in context: Compare them to results of others (refer explicitly to the references).
			\item Introduction: \vspace{-0.1cm}
				\begin{itemize} \itemsep -1pt
				\item This should make it clear to the expert reviewer that you know your area and what others have done
				\item Discuss the state-of-the-art in terms of what others have done recently. Make use of references.
				\item What is the problem you want to solve?
				\item Capture the different approaches to solving the problem and show which of these approaches you have picked and why.  
				\item Continue with explaining your approach
				\end{itemize}
			\item Plan [the main body of the paper] in advance (like a system architecture): \vspace{-0.1cm}
				\begin{itemize} \itemsep -1pt
				\item List 2-to-3 innovative aspects.
				\item Explain the importance of these aspects in terms of new design, performance achievements, how it advances the state-of-the-art.
				\end{itemize}
			\item Body of the paper: \vspace{-0.1cm}
				\begin{itemize} \itemsep -1pt
				\item This should focus on the key ideas and build up the paper incrementally.
				\item Use a figure or diagram to show your approach.
				\item Preferably, show circuit schematics and explain how the circuit works and what is new about it.  
				\item Show measurement results: \vspace{-0.1cm}
					\begin{itemize} \itemsep -1pt
					\item If needed, summarize results in a table format.
					\item If appropriate, provide a Figure-of-Merit to prove that your work advances the state-of-the-art.
					\end{itemize}
				\end{itemize}
			\item Compare your results with those of others: \vspace{-0.1cm}
				\begin{itemize} \itemsep -1pt
				\item Be straightforward in the comparison.
				\item Do not ignore bad results; discuss and explain any shortcomings, rather than ignoring them.
				\item Compare your results with a paper that uses a similar test technique, and which deals with a similar system.
				\end{itemize}
			\item Conclusion: \vspace{-0.1cm}
				\begin{itemize} \itemsep -1pt
				\item Highlight the results.
				\item The final or pre-final paragraph should list all important measured results, give the reviewers a complete picture of your system and convince them of the technical accuracy of your results.
				\item Mention how your results advance the state-of-the-art.
				\end{itemize}
			\item Title of the paper: \vspace{-0.1cm}
				\begin{itemize} \itemsep -1pt
				\item It should give a good idea of the paper's contents and highlights. Do NOT make the title too broad or general, since it may appear to be a marketing paper.
				\item Eg, when your paper talks about Cache and how the Cache is built, do NOT use a title like ``High-speed processors,'' but use a title like ``A fast Cache for a High-Speed Processor''
				\item Or, use a title like ``An 800mW 10Gb$/$s Ethernet Transceiver in 0.13$\mu$m CMOS,'' and NOT: ``A novel, high-speed transceiver''
				\end{itemize}
			\item Body of the paper: \vspace{-0.1cm}
				\begin{itemize} \itemsep -1pt
				\item Don't repeat too much of the abstract. 
				\item Don't present much theory; Refer to other sources of such material in a reference. 
				\item Don't give too many equations; This is not a Ph.D. thesis, and hence only relevant equations should be stated, if any. If an equation is used, you must explain the equation. Don't make assumptions. Everyone has a different way of interpreting such information.
				\item Don't write a tutorial-type paper. ISSCC papers must be very concise and innovative.
				\end{itemize}
			\item Technical content -- innovation is key: \vspace{-0.1cm}
				\begin{itemize} \itemsep -1pt
				\item Highlight the INNOVATION in your paper, early on. Innovation can include one or more of the following: \vspace{-0.1cm}
					\begin{itemize} \itemsep -1pt
					\item Scalability
					\item circuit or architecture innovation
					\item implementation of a new system approach
					\item use of a new technology
					\item best-performance reported
					\end{itemize}
				\item Address the innovation aspect clearly: \vspace{-0.1cm}
					\begin{itemize} \itemsep -1pt
					\item What is new
					\item Accuracy of the proposed approach, circuit, or system
					\item Solutions to the problem
					\item Feasibility of implementation
					\item Comparison with previously proposed techniques
					\end{itemize}
				\item Show at least one important circuit diagram.
				\item When showing a circuit or diagram: \vspace{-0.1cm}
					\begin{itemize} \itemsep -1pt
					\item Explain what is new about it (give an explanation beyond that of a data sheet)
					\item Explain its operation. Do not expect the reviewer to dissect it. Help the reviewer to understand its operation. But, be concise and brief.
					\item What are the advantages, what are the shortcomings? 
					\end{itemize}
				\item Replace words like ``Fastest,'' ``Smallest,'' ``Lowest power consumption,'' etc, by quantitative and accurate comparisons with earlier work. 
				\item Make sure you mention each reference. Include also pending publications at conferences or in journals that appear before ISSCC (see also pre-publication policy)
				\end{itemize}
			\item Stating and describing experimental results in the paper: \vspace{-0.1cm}
				\begin{itemize} \itemsep -1pt
				\item Include a die photo, and give the chip size and technology used.
				\item Include measurements of the fabricated chip, I-V curves, power, etc. Be precise and quantitative.
				\item Compare measured results against stated requirements, and to prior art.
				\item Include a summary table of the design that highlights the specification and performance metrics. 
				\end{itemize}
			\item Do not submit: \vspace{-0.1cm}
				\begin{itemize} \itemsep -1pt
				\item A paper that gives only simulations and has no silicon implementation and test results.
				\item A paper with only modeling and/or equations: submit these to ISCAS, ICCAD or DAC.
				\item A paper that is outside the scope of ISSCC topics. 
				\item Work that has been published somewhere else.
				\end{itemize}
			\item Common reasons for paper rejection: \vspace{-0.1cm}
				\begin{itemize} \itemsep -1pt
				\item A lack of clear evidence of what is novel in the work, and the extent to which it advances the state-of-the-art. 
				\item Successful submissions contain specific new results with sufficient detail and data to be understood, with schematics and measured results for key circuits, when appropriate.
				\item Wrong conference, or pre-publication. 
				\end{itemize}
			\item Pre-publication: \vspace{-0.1cm}
				\begin{itemize} \itemsep -1pt
				\item If a substantial part of a paper has been published before the upcoming ISSCC, the paper will not be accepted. This is the case when: \vspace{-0.1cm}
					\begin{itemize} \itemsep -1pt
					\item Disclosure of the innovative circuitry, architectures, algorithms, etc, occurs in articles, data sheets, trade journals, or other conferences.
					\item Any detailed disclosure of innovative technical ideas on the World-Wide Web before the paper presentation at the Conference will be considered pre-publication.
					\end{itemize}
				\end{itemize}
			\item Pre-publication policy: \vspace{-0.1cm}
				\begin{itemize} \itemsep -1pt
				\item However, a paper may be acceptable in cases where: \vspace{-0.1cm}
					\begin{itemize} \itemsep -1pt
					\item The chip has been sampled, entered production, and/or appeared in a publication that addressed only the marketing or applications aspects of the product.
					\item Disclosure consisting only of abbreviated data sheets that provide only specifications, a feature list, and a coarse block diagram. 
					\item The work has been presented at a workshop or niche conference with limited attendance and no published proceedings or press coverage.
					\end{itemize}
				\item After your paper has been accepted, DO NOT publish any details or summaries on the web, press releases or any other articles before the conference!
				\end{itemize}
			\item Pre-publication material: \vspace{-0.1cm}
				\begin{itemize} \itemsep -1pt
				\item If any material related to your ISSCC submission will have been published prior to the Conference, copies of these prior publications should be submitted.
				\item Such material includes data sheets, press releases, papers or abstracts submitted or accepted at another conference or in a journal appearing before the Conference, and any other forms of publication such as Web presentations.
				\end{itemize}
			\item In summary, it's all about: \vspace{-0.1cm}
				\begin{itemize} \itemsep -1pt
				\item innovation
				\item advancing state-of-the-art
				\item technical quality of the results
				\item results clearly explained
				\end{itemize}
			\end{enumerate}
		\item Editors of the {\it IEEE Journal of Solid-State Circuits}, ``JSSC Submission: Information for JSSC Authors''. Available online at: \url{http://ewh.ieee.org/soc/sscs/index.php?option=com_content&task=view&id=72&Itemid=1}; last accessed on September 18, 2010.
		\item Bram Nauta, ``How to write a good Journal of Solid State Circuits paper,'' presentation slides for the IEEE Asian Solid-State Circuits Conference, Fukuoka, Japan, November 2008. Available online at: \url{http://sscs.ieee.org/images/files/education/how%2520to%2520write%2520jssc%2520paper-v3.pdf}; last accessed on December 28, 2010. \vspace{-0.1cm}
			\begin{enumerate} \itemsep -1pt
			\item Conference papers can get accepted or rejected if they are incomplete or lack key references.
			\item Special issues on IEEE Solid-State Circuits Society conferences: \vspace{-0.1cm}
				\begin{itemize} \itemsep -1pt
				\item December -- ISSCC-analog, RF (issue)
				\item January -- ISSCC-dig+rest (issue)
				\item April -- VLSI (issue)
				\item May -- RFIC (section)
				\item July -- ESSCIRC (issue)
				\item August -- CICC (issue)
				\item September -- BCTM (section)
				\item October -- CSIC (section)
				\item November -- A-SSC (section)
				\end{itemize}
			\item The title of the paper: \vspace{-0.1cm}
				\begin{itemize} \itemsep -1pt
				\item Must describe the paper
				\item Not too vague: \vspace{-0.1cm}
					\begin{itemize} \itemsep -1pt
					\item ``A novel receiver'' -- Do not use ``novel'' anyway
					\item ``5-GHz RF Frontends for Ultra-Low-Voltage and Ultra-Low-Power Operations'' -- How much is is Ultra?
					\end{itemize}
				\item But exactly what is really new -- ``Noise canceling technique for wideband receivers''
				\item Or exactly what is achieved -- ``A 1.5GHz 1.3dB NF, 10mW down converter in 65nm CMOS for GPS applications''
				\item Or both!
				\end{itemize}
			\item Introduction: \vspace{-0.1cm}
				\begin{itemize} \itemsep -1pt
				\item Describe the problem you solve: open the subject; zoom in step by step; describe your assumptions; \& each step is one paragraph
				\item Describe the state-of-the-art: use plenty of references
				\item Tell your basic idea: \vspace{-0.1cm}
					\begin{itemize} \itemsep -1pt
					\item This motivates the reader to continue reading.
					\item Cite your prepublications and tell the difference
					\end{itemize}
				\item Give outline
				\end{itemize}
			\item The body: \vspace{-0.1cm}
				\begin{itemize} \itemsep -1pt
				\item Explain your key idea
				\item Build up step by step: \vspace{-0.1cm}
					\begin{itemize} \itemsep -1pt
					\item one thinking step at a time
					\item each step is one paragraph
					\end{itemize}
				\item Proof that it makes sense: \vspace{-0.1cm}
					\begin{itemize} \itemsep -1pt
					\item Use mathematics
					\item Give exactly your boundary conditions
					\item Give experimental results in a comprehensive way
					\end{itemize}
				\item Be self-critical and realistic: Does it really make sense?
				\item E.g., for a linearity improvement technique: \vspace{-0.1cm}
					\begin{itemize} \itemsep -1pt
					\item If power dissipation is larger
					\item And noise is also larger
					\item And you know that {\it P} $\sim$ {\it SNR}: Does this make sense?
					\end{itemize}
				\item Is it just the technology or your smartness? E.g., speed $\sim f_{T}$ or $f_{\rm max}$
				\item Are practical boundary conditions met? VCO at high frequency but $P_{\rm out} = -30 {\rm dBm}$.
				\end{itemize}
			\item Experimental results: \vspace{-0.1cm}
				\begin{itemize} \itemsep -1pt
				\item Describe exactly what has been measured and how: \vspace{-0.1cm}
					\begin{itemize} \itemsep -1pt
					\item describe setup
					\item ``Bio biased''? (manual tweaking and tuning)
					\item probe or PCB?
					\item What equipment?
					\item How many samples?
					\item PVT?
					\item Batch to batch spread?
					\end{itemize}
				\item Experiment must be repeatable and of practical use (e.g., for industry)
				\item compare with theory/simulations
				\item Does it prove your idea and theory?
				\item Always indicate if a result is measured, simulated, or calculated
				\item ``Figure X shows the noise figure versus frequency'' Is this measured? Simulated? Calculated? Estimated?
				\end{itemize}
			\item IC realization: \vspace{-0.1cm}
				\begin{itemize} \itemsep -1pt
				\item Give chip photograph: \vspace{-0.1cm}
					\begin{itemize} \itemsep -1pt
					\item dimensions
					\item What is what?
					\end{itemize}
				\item Give technology + options: e.g., state the process technology used to manufacture the chip
				\end{itemize}
			\item Discuss results: \vspace{-0.1cm}
				\begin{itemize} \itemsep -1pt
				\item compare to state-of-the-art in a fair way: \vspace{-0.1cm}
					\begin{itemize} \itemsep -1pt
					\item show all relevant data and papers
					\item A table can help, although measurements are hard to compare
					\end{itemize}
				\item Use common figure-of-merit (FoM) definitions: e.g., determine the common FoM for ADCs, VCOs, and filters
				\item Be careful to define your own FoM: \vspace{-0.1cm}
					\begin{itemize} \itemsep -1pt
					\item do not misuse FoM for showing off
					\item Power $\sim$ SNR. BW makes sense
					\item Power/bondpad is NOT a good FoM!!
					\end{itemize}
				\item Help the reader to interpret the results
				\item Absolute accuracy needed? Show many samples, and proof batch to batch robustness
				\item Matching needed? Show many samples
				\item Calibrated circuits? Describe what input signal is used/required. When does it go wrong? How realistic is it?
				\end{itemize}
			\item Conclusions: \vspace{-0.1cm}
				\begin{itemize} \itemsep -1pt
				\item Start writing with this
				\item First, make a bullet list for yourself: \vspace{-0.1cm}
					\begin{itemize} \itemsep -1pt
					\item A handful of bullets
					\item So you know where to write towards
					\item This gives your paper focus
					\end{itemize}
				\item The Conclusion should be readable without reading the whole paper
				\item Convince the reader: What did we learn?
				\end{itemize}
			\item References: \vspace{-0.1cm}
				\begin{itemize} \itemsep -1pt
				\item Include latest state of the art: for benchmark
				\item But, also refer to the original papers: \vspace{-0.1cm}
					\begin{itemize} \itemsep -1pt
					\item Go back in time!
					\item Most references are younger than 5 years
					\item While most ideas are much older
					\end{itemize}
				\item Textbooks are useful too
				\end{itemize}
			\item General Writing Tips: \vspace{-0.1cm}
				\begin{itemize} \itemsep -1pt
				\item A well-written paper gives the impression of a good idea
				\item If a paper is too complex: \vspace{-0.1cm}
					\begin{itemize} \itemsep -1pt
					\item Reviewers don't understand it
					\item Reviewers don't believe it
					\item Reviewers will not like it
					\end{itemize}
				\item If a paper is too simplistic: \vspace{-0.1cm}
					\begin{itemize} \itemsep -1pt
					\item Reviewers think its nothing special
					\item Even if the results are good
					\end{itemize}
				\item Make your problem relevant
				\item Start with the ``big picture''
				\item Take the reader by the hand: step by step explanation
				\item Highlight innovation
				\item Do not give too much theoretical details
				\item Do not try to make a tutorial
				\item Do not use ``very'' but give the numbers
				\item Avoid using the word ``novel''; everything that you don't cite should be novel
				\item Use short sentences
				\item Use simple words
				\item One point per paragraph: \vspace{-0.1cm}
					\begin{itemize} \itemsep -1pt
					\item First of last sentence is most important
					\item The rest is explanation
					\end{itemize}
				\item If you are stuck: \vspace{-0.1cm}
					\begin{itemize} \itemsep -1pt
					\item Tell a friend what you did
					\item Use the words and slides like on your conference paper
					\item Polish the text later
					\end{itemize}
				\item Let a fellow student read and comment
				\item Ask native speaker to correct language
				\item Polish, polish, polish: \vspace{-0.1cm}
					\begin{itemize} \itemsep -1pt
					\item reviewers hate mistakes
					\item ``It iz raely anojing to raed tekst width misstakes''
					\end{itemize}
				\end{itemize}
			\item Figures: \vspace{-0.1cm}
				\begin{itemize} \itemsep -1pt
				\item Make the figures look like a cartoon: \vspace{-0.1cm}
					\begin{itemize} \itemsep -1pt
					\item Reader can understand idea by looking at figures and caption only
					\end{itemize}
				\item Spend a lot of time making good figures: \vspace{-0.1cm}
					\begin{itemize} \itemsep -1pt
					\item Papers with bad figures almost always get rejected
					\end{itemize}
				\item Must be readable in single column
				\item Avoid placing figures in double columns	
				\end{itemize}
			\item Do not: \vspace{-0.1cm}
				\begin{itemize} \itemsep -1pt
				\item Publish the same material elsewhere. Reviewers and readers always see this. This is unethical.
				\item Change your paper after acceptance and before publication: \vspace{-0.1cm}
					\begin{itemize} \itemsep -1pt
					\item E.g., remove reference to competitor
					\item Reviewers always see this
					\end{itemize}
				\item Use someone else's ideas: ``Someone else'' is reading too
				\item Hide ``unpleasant'' measurements
				\item Fabricate or falsify results: \vspace{-0.1cm}
					\begin{itemize} \itemsep -1pt
					\item Do not tune bias for each measuring point
					\item Do not make a few chips and measure different parameters on different chips
					\item Or even completely falsify results
					\end{itemize}
				\end{itemize}
			\item In summary: \vspace{-0.1cm}
				\begin{itemize} \itemsep -1pt
				\item Needs an innovative idea: \vspace{-0.1cm}
					\begin{itemize} \itemsep -1pt
					\item Working silicon is not enough
					\item Must improve state-of-the-art
					\end{itemize}
				\item Needs new material after prepublication
				\item Reviewers are demanding
				\item Your writing technique can help improve the paper's chances of getting accepted for publication
				\end{itemize}
			\end{enumerate}
		\end{enumerate}
	\end{enumerate}
\item University of California, Berkeley: \vspace{-0.3cm}
	\begin{enumerate} \itemsep -2pt
	\item Department of City and Regional Planning; College of Environmental Design: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item Alvaro Huerta, {\it Resources: Writing \& Research Links / Attachments}, Department of City and Regional Planning, College of Environmental Design, University of California, Berkeley, 2010. Available online at: \url{http://sites.google.com/site/alvarohuertasite/links-academic-more}; last accessed on January 5, 2010.
		\end{enumerate}
	\end{enumerate}
\item Stanford University: \vspace{-0.3cm}
	\begin{enumerate} \itemsep -2pt
	\item Stanford University InfoLab: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item Prof. Jennifer Widom: \url{http://infolab.stanford.edu/~widom/paper-writing.html}
		\end{enumerate}
	\end{enumerate}
\item Carnegie Mellon University: \vspace{-0.3cm}
	\begin{enumerate} \itemsep -2pt
	\item Philip Koopman, ``How to Write an Abstract,'' Department of Electrical and Computer Engineering, Carnegie Mellon University, October 1997. Available at: \url{http://www.ece.cmu.edu/~koopman/essays/abstract.html}; last accessed on August 26, 2010. Also available at: \url{http://www.computersciencestudent.com/Extras/Abstract.html}.
	\end{enumerate}
\item University of Washington: \vspace{-0.3cm}
	\begin{enumerate} \itemsep -2pt
	\item Department of Mathematics: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item Minh Van Nguyen, {\it Academia}, Department of Mathematics, University of Washington, 2010. Available online at: \url{http://sage.math.washington.edu/home/mvngu/academia.html}; last accessed on October 25, 2010.
		\end{enumerate}
	\end{enumerate}
\item University of Pennsylvania: \vspace{-0.3cm}
	\begin{enumerate} \itemsep -2pt
	\item Steve Zdancewic, ``Writing Tips,'' Department of Computer and Information Science, School of Engineering and Applied Science, University of Pennsylvania, July 29, 2003. Available at: \url{http://www.cis.upenn.edu/~stevez/writing-tips.html}; last accessed on September 5, 2010.
\item University of California, Los Angeles: \vspace{-0.3cm}
	\end{enumerate}
	\begin{enumerate} \itemsep -2pt
	\item Terence Tao, {\it On writing}, Department of Mathematics, University of California, Los Angeles. Available at: \url{http://terrytao.wordpress.com/advice-on-writing-papers/}; last accessed on September 1, 2010.
	\end{enumerate}
\item Purdue University: \vspace{-0.3cm}
	\begin{enumerate} \itemsep -2pt
	\item Purdue Online Writing Lab (OWL): \url{http://owl.english.purdue.edu/owl/}
	\end{enumerate}
\item Royal Institute of Technology (KTH): \vspace{-0.3cm}
	\begin{enumerate} \itemsep -2pt
	\item Department of Microelectronics and Information Technology; Laboratory of Electronics and Computer Systems: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item Elena Dubrova, ``The Art of Doctoral Research,'' (FIL3001, PhD course, 7.5 pt), Sept. 2008 - May 2009. Available at: \url{http://web.it.kth.se/~dubrova/coursePhD.html}; last accessed on September 14, 2010.
		\end{enumerate}
	\end{enumerate}
\item University of California, Davis: \vspace{-0.3cm}
	\begin{enumerate} \itemsep -2pt
	\item Office of Student Judicial Affairs: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item Publications: \url{http://sja.ucdavis.edu/publications.html}
		\end{enumerate}
	\end{enumerate}
\item Pennsylvania State University: \vspace{-0.3cm}
	\begin{enumerate} \itemsep -2pt
	\item Penn State College of Engineering: \url{http://www.writing.engr.psu.edu/}
	\end{enumerate}
\item University of Toronto: \vspace{-0.3cm}
	\begin{enumerate} \itemsep -2pt
	\item University College (UC) Writing Centre: \url{http://www.utoronto.ca/ucwriting/handouts.html}
	\end{enumerate}
\item Link{\"{o}}ping University: \vspace{-0.3cm}
	\begin{enumerate} \itemsep -2pt
	\item Department for Computer and Information Science: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item Christoph Kessler, ``Stylistic advice to my exjobb and PhD students for writing a thesis,'' Department for Computer and Information Science, Link{\"{o}}ping University. Available at: \url{http://www.ida.liu.se/~chrke/exjobb/writing.html}; last accessed on September 1, 2010.
		\item Christoph Kessler, ``Exjobb project plan guidelines,'' Department for Computer and Information Science, Link{\"{o}}ping University. Available at: \url{http://www.ida.liu.se/~chrke/exjobb/exj_plan.shtml}; last accessed on September 1, 2010. [ This provides information on writing research/thesis proposals. ]
		\end{enumerate}
	\end{enumerate}
\item University of Crete: \vspace{-0.3cm}
	\begin{enumerate} \itemsep -2pt
	\item Department of Computer Science: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item Panagiota Fatourou: \vspace{-0.1cm}
			\begin{enumerate} \itemsep -1pt
			\item \url{http://www.ics.forth.gr/~faturu/}
			\item American Mathematical Society, ``A Manual for Authors of Mathematical Papers.'' Available online at: \url{http://www.ams.org/journals/bull/1943-49-03/S0002-9904-1943-07884-6/S0002-9904-1943-07884-6.pdf}; last accessed on December 22, 2010.
			\end{enumerate}
		\end{enumerate}
	\end{enumerate}
\item University of Cambridge: \vspace{-0.3cm}
	\begin{enumerate} \itemsep -2pt
	\item University Offices -- Unified Administrative Services / The Old Schools: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item University Offices, ``Information for students,'' University of Cambridge, November 30, 2010. Available online at: \url{http://www.admin.cam.ac.uk/univ/plagiarism/students/}; last accessed on January 8, 2010.
		\end{enumerate}
	\end{enumerate}
\item University College London: \vspace{-0.3cm}
	\begin{enumerate} \itemsep -2pt
	\item Department of Medical Physics \& Bioengineering: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item Adam Gibson, {\it Teaching links: Tips on how to write scientific articles}, Department of Medical Physics \& Bioengineering, University College London, October 8, 2008. Available online at: \url{http://www.medphys.ucl.ac.uk/~agibson/work/history.html#writing}; last accessed on October 21, 2010. [ Also available at: \url{http://www.ucl.ac.uk/medphys/staff/people/agibson/www/teaching/#writing}]
		\end{enumerate}
	\end{enumerate}
\item Swarthmore College: \vspace{-0.3cm}
	\begin{enumerate} \itemsep -2pt
	\item Department of History: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item Timothy Burke, ``Beyond the Five-Paragraph Essay,'' in his blog {\it Easily Distracted: Culture, Politics, Academia and Other Shiny Objects}, Department of History, Swarthmore College. Available at: \url{http://weblogs.swarthmore.edu/burke/permanent-features-advice-on-academia/beyond-the-five-paragraph-essay/}; last accessed on September 14, 2010.
		\item Timothy Burke, ``How to Read in College -- Staying Afloat: Some Scattered Suggestions on Reading in College,'' in his blog {\it Easily Distracted: Culture, Politics, Academia and Other Shiny Objects}, Department of History, Swarthmore College. Available at: \url{http://weblogs.swarthmore.edu/burke/permanent-features-advice-on-academia/how-to-read-in-college/}; last accessed on September 14, 2010.
		\end{enumerate}
	\end{enumerate}
\item Indiana University: \vspace{-0.3cm}
	\begin{enumerate} \itemsep -2pt
	\item Writing Tutorial Services: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item \url{http://www.indiana.edu/~wts/}
		\item WTS Pamphlets: \url{http://www.indiana.edu/~wts/pamphlets.shtml}
		\end{enumerate}
	\end{enumerate}
\item University of Alberta: \vspace{-0.3cm}
	\begin{enumerate} \itemsep -2pt
	\item Faculty of Arts: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item Centre for Writers: \vspace{-0.1cm}
			\begin{enumerate} \itemsep -1pt
			\item Centre for Writers Resources: \url{http://www.c4w.arts.ualberta.ca/Resources/Resource.aspx}
			\item Other Writing Centres: \url{http://www.c4w.arts.ualberta.ca/OtherWritingCentres/OtherWritingCentres.aspx}
			\end{enumerate}
		\end{enumerate}
	\end{enumerate}
\item Universit{\'{e}} du Qu{\'{e}}bec {\`{a}} Montr{\'{e}}al (UQAM, University of Quebec): \vspace{-0.3cm}
	\begin{enumerate} \itemsep -2pt
	\item Pavillon Saint-Urbain, LICEF Research Center: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item Daniel Lemire, ``Write Good Papers,'' in {\it Daniel Lemire's blog}, LICEF Research Center, Pavillon Saint-Urbain, Universit{\'{e}} du Qu{\'{e}}bec {\`{a}} Montr{\'{e}}al. Available at: \url{http://www.daniel-lemire.com/blog/rules-to-write-a-good-research-paper/}; last accessed on September 14, 2010.
		\end{enumerate}
	\end{enumerate}
\item State University of New York at Buffalo: \vspace{-0.3cm}
	\begin{enumerate} \itemsep -2pt
	\item William J. Rapaport, ``How to Write (How to Prepare Technical Reports),'' Department of Computer Science and Engineering, State University of New York at Buffalo, Buffalo, NY. Available at: \url{http://www.cse.buffalo.edu/~rapaport/howtowrite.html}; last accessed on August 25, 2010.
	\end{enumerate}
\item Tufts University: \vspace{-0.3cm}
	\begin{enumerate} \itemsep -2pt
	\item Norman Ramsey, {\it Norman Ramsey's Resources for Writers}, Department of Computer Science, Tufts University. Available at: \url{http://www.cs.tufts.edu/~nr/students/writing.html}; last accessed on September 2, 2010.
	\end{enumerate}
\item University of Maryland, Baltimore County: \vspace{-0.3cm}
	\begin{enumerate} \itemsep -2pt
	\item Department of Computer Science and Electrical Engineering: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item Alan T. Sherman (Alan Theodore Sherman), ``Some Advice on Writing a Technical Report,'' Department of Computer Science and Electrical Engineering, University of Maryland, Baltimore County, April 27, 1996. Available at: \url{http://www.csee.umbc.edu/~sherman/Courses/documents/TR_how_to.html}; last accessed on August 28, 2010.
		\end{enumerate}
	\end{enumerate}
\item University of Maryland, College Park: \vspace{-0.3cm}
	\begin{enumerate} \itemsep -2pt
	\item Department of Computer Science: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item Neil Spring, ``style-check.rb,'' Department of Computer Science, University of Maryland, College Park, December 1, 2007. Available at: \url{http://www.cs.umd.edu/~nspring/software/style-check-readme.html}; last accessed on September 14, 2010.
		\item Neil Spring, ``Advising Notes,'' Department of Computer Science, University of Maryland, College Park. Available at: \url{http://www.cs.umd.edu/~nspring/advising.html}; last accessed on September 14, 2010.
		\end{enumerate}
	\end{enumerate}
\item Missouri University of Science and Technology (formerly University of Missouri-Rolla): \vspace{-0.3cm}
	\begin{enumerate} \itemsep -2pt
	\item Writing Across the Curriculum Program: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item Includes the Moeller Writing Center, and the Center for Writing Technologies
		\item \url{http://writingcenter.mst.edu/}
		\item {\it Writing Center Documentation Style Guides} and {\it Writing Center Helpful Handouts}: \vspace{-0.1cm}
			\begin{enumerate} \itemsep -1pt
			\item \url{http://writingcenter.mst.edu/writinghandouts.html}
			\item It includes the following documentation style guides: \vspace{-0.1cm}
				\begin{itemize} \itemsep -1pt
				\item American Society of Civil Engineers (ASCE) Documentation Style
				\item American Society of Mechanical Engineers (ASME) Publication Information
				\item American Psychological Association (APA) Documentation Style
				\item Chicago Manual of Style Documentation I - author/date
				\item Chicago Manual of Style Documentation II - notes/bibliography
				\item Institute of Electrical and Electronics Engineers (IEEE) Documentation Style
				\item Modern Language Association (MLA) Documentation Style
				\end{itemize}
			\end{enumerate}
		\end{enumerate}
	\end{enumerate}
\item Colorado State University: \vspace{-0.3cm}
	\begin{enumerate} \itemsep -2pt
	\item Department of Electrical \& Computer Engineering; College of Engineering: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item Edwin K. P. Chong, ``Edwin Chong's links of interest,'' Department of Electrical \& Computer Engineering, College of Engineering, Colorado State University, October 18, 2010. Available online at: \url{http://www.engr.colostate.edu/~echong/links.shtml}; last accessed on November 3, 2010.
		\end{enumerate}
	\end{enumerate}
\item Wright State University: \vspace{-0.3cm}
	\begin{enumerate} \itemsep -2pt
	\item University College; University Writing Center: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item Writing Center Style Guide: \url{http://www.wright.edu/uc/success/services/writingctr/styleguidefaq.html}
		\item Academic Writing: \url{http://www.wright.edu/uc/success/services/writingctr/academicwriting.html}
		\item Plagiarism: \url{http://www.wright.edu/uc/success/services/writingctr/plagiarism.html}
		\item Thesis Statements: \url{http://www.wright.edu/academics/writingctr/resources/thesisstatements.html}
		\item Writer Resources: \url{http://www.wright.edu/academics/writingctr/resources/}
		\item University Writing Center, University College, Wright State University
		\end{enumerate}
	\item Writing Across the Curriculum (WAC) program: \url{http://www.wright.edu/academics/wac/}
	\item Department of English Language and Literature, College of Liberal Arts: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item Department of English Language and Literature, {\it WSU Writing Web: Citation Resources}, Department of English Language and Literature, College of Liberal Arts, Wright State University. Available at: \url{http://www.wright.edu/cola/Dept/eng/wsuwweb/pageindxs/citation.htm}; last accessed on September 14, 2010.
		\end{enumerate}
	\end{enumerate}
\item Capital Community College: \vspace{-0.3cm}
	\begin{enumerate} \itemsep -2pt
	\item Guide to Grammar and Writing: \url{http://grammar.ccc.commnet.edu/grammar/}
	\item Online Resources for Writers: \url{http://webster.commnet.edu/writing/writing.htm}
	\end{enumerate}
\item TAFE NSW (Technical and Further Education, New South Wales): \vspace{-0.3cm}
	\begin{enumerate} \itemsep -2pt
	\item The Information Centre, {\it Study Skills: Writing Skills}, The Information Centre, The Learning Centre, North Coast Institute, TAFE NSW (Technical and Further Education, New South Wales): \url{http://www.ncistudent.net/StudySkills/WritingSkills/Introduction.htm}
	\end{enumerate}
\item IBM: \vspace{-0.3cm}
	\begin{enumerate} \itemsep -2pt
	\item Program Analysis Group; IBM T.J. Watson Research Center: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item Eran Yahav, {\it Resources: Writing Resources}, IBM. Available online at: \url{http://www.research.ibm.com/people/e/eyahav/resources.html}; last accessed on September 28, 2010. [ Also, see \url{http://www.research.ibm.com/people/e/eyahav/misc.html} under {\it misc: Resources} ]
		\end{enumerate}
	\end{enumerate}
\item The Chronicle of Higher Education: \vspace{-0.3cm}
	\begin{enumerate} \itemsep -2pt
	\item Michael C. Munger, ``10 Tips on How to Write Less Badly,'' in {\it Advice: Do Your Job Better}, The Chronicle of Higher Education, September 6, 2010. Available at: \url{http://chronicle.com/article/10-Tips-on-How-to-Write-Less/124268/}; last accessed on September 13, 2010.
	\end{enumerate}
\item {\it Guide to Online Schools}, or {\it GuideToOnlineSchools.com}: \vspace{-0.3cm}
	\begin{enumerate} \itemsep -2pt
	\item {\it The Ultimate Style Guide Resources for MLA, APA, Chicago, and CSE}. Available at: \url{http://www.guidetoonlineschools.com/tips-and-tools/mla-apa-chicago-cse}; last accessed on August 25, 2010.
	\item {\it The Complete Plagiarism Resource}. Available at: \url{http://www.guidetoonlineschools.com/tips-and-tools/plagiarism}; last accessed on August 25, 2010.
	\item {\it The Top 50 Academic Writing Resources Online}. Available at: \url{http://www.guidetoonlineschools.com/tips-and-tools/best-writing-resources}; last accessed on August 25, 2010.
	\end{enumerate}
\end{itemize}



Resources for improving my English language skills: \vspace{-0.3cm}
\begin{enumerate} \itemsep -4pt
\item RubyWorks (resource on English grammar): \url{http://rubyworks.github.com/english/grammar/gramdex.html}
\item U.S. Department of State: \vspace{-0.3cm}
	\begin{enumerate} \itemsep -2pt
	\item Bureau of Educational and Cultural Affairs: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item Materials for Teaching and Learning English: \url{http://exchanges.state.gov/englishteaching/resources-et.html}
		\end{enumerate}
	\end{enumerate}
\end{enumerate}




Resources for detecting plagiarism: \vspace{-0.3cm}
\begin{enumerate} \itemsep -4pt
\item PlagiarismDetect.com: \url{http://www.plagiarismdetect.com/}
\item Plagiarism Checker (by Darren Hom): \url{http://www.plagiarismchecker.com/}
\item ArticleChecker.com: \url{http://www.articlechecker.com/}
\item CheckForPlagiarism.net (by Plagiarism-Checkers, Inc.): \url{http://www.checkforplagiarism.net/}
\item Turnitin (by iParadigms, LLC): \url{http://www.turnitin.com}
\end{enumerate}














%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Resources for Postdoc Positions}
\label{resourcesforpostdocpositions}

Resources for postdoc positions: \vspace{-0.3cm}
\begin{enumerate} \itemsep -4pt
\item The Chronicle of Higher Education: \vspace{-0.3cm}
	\begin{enumerate} \itemsep -2pt
	\item Zoe Smith and Ariana Sutton-Grier, ``Making the Most of Your Postdoc,'' The Chronicle of Higher Education: Advice: Do Your Job Better, July 15, 2010. Available at: \url{http://chronicle.com/article/Making-the-Most-of-Your/66265/}; last accessed on September 6, 2010.
	\end{enumerate}
\item Inside Higher Ed: \vspace{-0.3cm}
	\begin{enumerate} \itemsep -2pt
	\item \url{http://www.insidehighered.com/}
	\item Has information concerning the application for faculty positions, and advice for career paths in higher education institutions. 
	\item Kerry Ann Rockquemore, ``Winning Tenure Without Losing Your Soul: Stop Talking, Start Walking,'' Inside Higher Ed: Career Advice, Inside Higher Ed, January 25, 2010. Available at: \url{http://www.insidehighered.com/advice/winning/winning2}; last accessed on September 7, 2010.
	\end{enumerate}
\item Nature Publishing Group (a division of Macmillan Publishers Limited): \vspace{-0.3cm}
	\begin{enumerate} \itemsep -2pt
	\item Kendall Powell, ``Careers and Recruitment: A foot in the door,'' in {\it Nature}, Vol. 463, No. 7281, pp. 696-697, February 4, 2010. Available online at: \url{http://dx.doi.org/10.1038/nj7281-696a}; last accessed on December 31, 2010. \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item I should commence looking for a postdoctoral research position early in my penultimate year.
		\item When looking for a postdoctoral research position, I shall take note of the name of research labs which journal/conference papers that I find are interesting. That is, each time I read an interesting journal/conference paper, take note of the name of the research labs and its affiliation (name of department, and organization/university).
		\item Compile a list of 20-30 research labs that I find are interesting. Pare down this list to about 5-6 labs, which I will apply to. Use the same heuristics for applying to graduate school. These 5-6 research labs shall include: \vspace{-0.1cm}
			\begin{enumerate} \itemsep -1pt
			\item A reach lab, which I want to be part of but may have difficulty securing a postdoctoral research position in
			\item 3-4 match/target labs, which postdocs and Ph.D. students are comparable to me in terms of research excellence, and which I shall have a good chance of securing a postdoctoral research position in
			\item 1-2 reliable/safety labs, which I should be able to secure a postdoctoral research position in
			\end{enumerate}
		\item Network with students at those labs in conferences, workshops, symposiums, and other events (such as ``summer schools''). Network with the principal/primary investigators (PIs) too!
		\item Make notes/summaries of poster presentations and talks from researchers in these labs.
		\item Make notes/summaries of their conference and journal papers. Try to get access to Ph.D. theses from their labs, and read them too. Pay special attention to the ``Future Work'' sections of the Ph.D. theses and conference papers.
		\item To secure a good postdoctoral research position, I must carry out ``diligent background research aimed to answer the question, `{\bf What do I want to get out of my postdoc?}'.''
		\item The question, ``What do I want to get out of my postdoc?,'' is analogous to the question for prospective Ph.D. students, ``What do I want to get out of my Ph.D. program?''
		\item ``Although they are short-term assignments, postdoc positions should be viewed as stepping stones to a longer-term independent career -- whether in academia, industry or another science-related post.''
		\item ``For that reason, it is hard to overstate the importance of the postdoc application. It is the fledgling scientist's bid to get noticed -- to gain a phone or in-person interview with labs. Background research, a carefully crafted curriculum vitae (CV) and cover letter, and personalization of each application will open doors. Form letters and typos will get applicants nowhere.''
		\item ``I wanted to apply to proven, top-notch labs where I was going to have the success and track record of the people coming out of these labs'' -- Toby Franks
		\item {\bf WARNING: Note that some postdoc positions require applications 12-18 months in advance.}
		\item Treat the process of applying for postdoctoral research positions like applying for R\&D jobs in the EDA/semiconductor industry. Apply to several positions simultaneously, so that I can interview in person with potential employers and lab colleagues prior to making my decision (about which offer of a postdoctoral research position to accept).
		\item ``An application typically consists of a cover letter introducing the applicant and his or her reasons for joining this particular lab; a CV outlining education, publication record, honors and accomplishments; and three referees who will provide supportive letters of recommendation on request. Some students also include a research summary of their graduate work; others incorporate this into their cover letter.''
		\item ``A little preparation goes a long way at this stage. Consider taking a workshop on writing cover letters and CVs, have senior colleagues review them, and proofread them carefully.''
		\item The cover letter and CV shall be free of mistakes.
		\item Things that PIs look for when hiring postdocs: \vspace{-0.1cm}
			\begin{enumerate} \itemsep -1pt
			\item First-author conference and journal publications, which prove that I ``can complete a project from start to finish'' as a junior scientist.
			\item Given the size of my home institution and resources available to my Ph.D. research lab, what have I accomplished? PIs want to see if Ph.D. students can accomplish a significant amount of things, despite the constraints in resources.
			\item List experiences that illustrate non-research responsibilities, including sitting on grad school or department committees, or hosting seminar speakers.
			\end{enumerate}
		\item ``Applicants should highlight what they hope to accomplish in general in a postdoc position. Specific details of projects should be left for the interview.''
		\item Quoted: Agneta Nordenskj{\"{o}}ld, a genetics researcher at the Karolinska Institute in Stockholm, advises spelling out your contributions to a graduate research project. ``Write it in a way that says, `I did this' or `My part of the project was', especially if you did something outstanding,'' she says.
		\item ``Those applying after taking a break from science must work harder to convince a lab head. Kristofor Langlais had been teaching high-school science at a ski academy in Vermont when he applied for postdoc positions in the Washington DC area.''
		\item ``After extensive research into each lab's publications, websites and even annual reports, he wrote his cover letters from the angle of someone already in the lab. He mentioned specific results he found interesting and the next natural steps the lab might take. ``I tried to make it sound like I could walk in that day and be self-sufficient immediately.'' He spent 20 hours or more on each application and his strategy paid off -- he had four phone interviews, and ended up in a molecular-genetics fellowship at the US National Institute of Child Health and Human Development in Bethesda, Maryland.''
		\item Quoted: Likewise, when Xiaoli Du was finishing up her doctorate at Peking Union Medical College in Beijing, she knew she would need to send applications to 30-40 labs if she wanted to obtain a postdoc in the United States. But she avoided the form-letter strategy. `` `Dear Professor' does not show respect or that you are really interested in their lab,'' she says. Instead, she personalized each application and stated how her training and experience would distinguish her from other applicants. Her hard work led to a postdoc at the US National Cancer Institute in Bethesda, Maryland. Du suggests attending international meetings to make first contact with potential advisers.
		\item Quoted: Few things, though, confer more of an advantage than secured funding. ``If a postdoc has their own fellowship, they can write their application to me in crayon and I'll take them,'' says Phil Baran, an organic chemist at the Scripps Research Institute in La Jolla, California. Unfunded applicants should assure the lab head that they have checked on specific fellowship possibilities and outline a plan to apply for them.
		\item Quoted: There are some definite `wrong ways' to apply. Goldstein, whose e-mail inbox is so overloaded that his system sends an automated response to direct queries to assistants and lab managers, says there is no room for red flags in the competitive arena. Avoid telling personal-life woes, bad-mouthing previous labs or advisers or expressing a desire to work at night so that you can surf during the day. Explain gaps in a CV or publication record.
		\item Quoted: ``Anything that signals the person is a prima donna, no matter how great they are, I don't go for,'' says Ken Yamada, laboratory chief at the National Institute of Dental and Craniofacial Research in Bethesda, Maryland. ``Research requires teamwork.''
		\item Quoted: Lab heads want a clear indication that applicants have carefully thought through their career goals and chosen this lab as the appropriate stepping stone. ``Does a genuine passion, drive, and hunger for research come through in their letters or on the phone?'' asks Yamada. ``Would they be doing the same thing if they were suddenly independently wealthy?''
		\item Postdoc application to-do list: \vspace{-0.1cm}
			\begin{enumerate} \itemsep -1pt
			\item Send your application by e-mail or overnight delivery. Consider a paper packet if you have unpublished manuscripts you want to include.
			\item Make it easy for lab heads to contact you by e-mail or phone.
			\item Follow-up by e-mail in 1-2 weeks to make sure they received your application. Don't phone.
			\item Choose referees who really know you, such as collaborators, unofficial advisers or others beyond the standard committee members.
			\item Meet with your referees to explain your career goals to them.
			\item Encourage referees to send their letters promptly (Salk Institute cell biologist Martin Hetzer says that the speed with which a letter lands in his inbox is usually much more telling than the letter's content).
			\item Prepare for the possibility of phone interviews, which may be scheduled or spontaneous. Make sure the conversation is two-way and ask your own questions, too. Have a list of bullet points handy in case you get nervous.
			\end{enumerate}
		\end{enumerate}
	\item Rania Sanford, ``How to navigate the road ahead,'' in {\it Nature}, Vol. 467, No. 7315, pp. 624, September 30, 2010. Available online at: \url{http://dx.doi.org/10.1038/nj7315-624a}; last accessed on December 31, 2010. \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item Check out how much mentoring is being provided to postdoctoral researchers (postdocs) by principal investigators (PIs).
		\item Check if the postdoc position allow me time to learn and seek guidance.
		\item Choose a research lab to do my postdoc, so that I can have a ``meaningful experience,'' obtain ``strong [research] results,'' and would be able to get ``a desirable job'' based on my postdoc research. Avoid research labs that don't allow me to satisfy these preferences.
		\item ``Good mentoring is an acquired skill.''
		\item Find out if the PI: \vspace{-0.1cm}
			\begin{enumerate} \itemsep -1pt
			\item Is aware of ``the stages in developing a mentoring relationship''
			\item Coaches students and postdocs, rather than supervises them
			\item ``Build[s] trust with prot{\'{e}}g{\'{e}}s and postdocs' expectations''
			\item Replicates the style of mentoring to all her/his mentees. Mentoring should be individualized/customized, since each person is a unique individual and differences exist between cultures, genders, and generations.
			\end{enumerate}
		\item Find out if the institution/university penalizes postdocs who have their own funding or fellowships (including competitive awards). The institution/university may provide medical insurance and other benefits to postdocs who are funded by research grants; hence, they are treated as staff members. If postdocs have their own funding or fellowships, they may not be eligible for medical insurance and other benefits that are provided by the university.
		\item Find out if support is given to non-US residents with regards to applying for non-immigrant J-1 visas or equivalent, relocation to the university's community, and assimilation into the university's community.
		\end{enumerate}
	\item Katharine Sanderson, ``Training: The career doctor,'' in {\it Nature}, Vol. 467, No. 7315, pp. 623, September 30, 2010. Available online at: \url{http://dx.doi.org/10.1038/nj7315-623a}; last accessed on December 31, 2010.
	\item Karen Kaplan, ``Careers and Recruitment: Industrial endeavours,'' in {\it Nature}, Vol. 461, No. 7263, pp. 554--555 September 24, 2009. Available online at: \url{http://dx.doi.org/10.1038/nj7263-554a}; last accessed on December 31, 2010. [ Has information on industrial postdoctoral research positions in the biotech industry. ]
	\item {\it naturejobs.com}: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item Career toolkit: \vspace{-0.1cm}
			\begin{enumerate} \itemsep -1pt
			\item Podcasts ({\it Naturejobs} podcasts): \vspace{-0.1cm}
				\begin{itemize} \itemsep -1pt
				\item Available online at: \url{http://www.nature.com/naturejobs/career-toolkit/podcasts/index.html}; last accessed on December 31, 2010.
				\end{itemize}
			\end{enumerate}
		\end{enumerate}
	\end{enumerate}
\item National Postdoctoral Association: \vspace{-0.3cm}
	\begin{enumerate} \itemsep -2pt
	\item Resources on Becoming a Postdoc: \url{http://www.nationalpostdoc.org/graduate-students}
	\item Faculty \& Administrators: \url{http://www.nationalpostdoc.org/faculty-administrators}
	\item Diversity Programs \& Resources: \url{http://www.nationalpostdoc.org/diversity-issues}
	\item International Postdocs: \url{http://www.nationalpostdoc.org/international-issues}
	\item The NPA Postdoctoral Core Competencies Toolkit (NPA Core Competencies): \url{http://www.nationalpostdoc.org/competencies}
	\end{enumerate}
\item Research Foundation -- Flanders (FWO), or ``Fonds voor Wetenschappelijk Onderzoek -- Vlaanderen'' (FWO): \vspace{-0.2cm}
	\begin{enumerate} \itemsep -2pt
	\item See \url{http://www.fwo.be/en/index.aspx}
	\item This is sponsored by the National Fund for Scientific Research (Belgium) 
	\item Research Foundation - Flanders (FWO): five-yearly prizes: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item Two Dr. A. De Leeuw-Damry-Bourlart prizes (100,000 Euro): For exact and applied sciences.
		\item Two Dr. Joseph Maisin prizes: For fundamental biomedical sciences and clinical biomedical sciences.
		\item The Ernest John Solvay prize: For humanities and social sciences.
		\end{enumerate}
	\item The Research Foundation  Flanders (FWO) pays a researchers income for the following categories: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item Ph.D. student
		\item Postdoctoral researcher
		\item Clinical fellowship
		\end{enumerate}
	\end{enumerate}
\item {\it PhDjobs.com}: \url{http://www.phdjobs.com/}
\item {\it innovation report}: \vspace{-0.3cm}
	\begin{enumerate} \itemsep -2pt
	\item Jobs (in industry and academia): \url{http://www.innovations-report.com/jobs/jobs.php}
	\end{enumerate}
\item Princeton University: \vspace{-0.3cm}
	\begin{enumerate} \itemsep -2pt
	\item Department of Computer Science, School of Engineering and Applied Science (SEAS): \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item Jeff Erickson and Boaz Barak, {\it TCS opportunities: Postdocs and other positions in theoretical computer science}, Center for Computational Intractability, Department of Computer Science, School of Engineering and Applied Science (SEAS), Princeton University. Available at: \url{http://intractability.princeton.edu/jobs/}; last accessed on September 15, 2010.
		\end{enumerate}
	\end{enumerate}
\item Simons Foundation: Simons Postdoctoral Fellows Program, \url{https://simonsfoundation.org/funding-guidelines/simons-postdoctoral-fellows-program}
\item IBM Postdoctoral Fellowships: \vspace{-0.3cm}
	\begin{enumerate} \itemsep -2pt
	\item IBM Herman Goldstine Postdoctoral Fellowship in Mathematical and Computer Sciences; see \url{http://domino.research.ibm.com/comm/research_projects.nsf/pages/goldstine.index.html}
	\item Josef Raviv Memorial Postdoctoral Fellowship; see \url{http://domino.research.ibm.com/comm/research.nsf/pages/d.compsci.josef.raviv.general.info.html}, \url{http://domino.research.ibm.com/comm/research.nsf/pages/d.compsci.raviv.winner.html}, and \url{http://domino.research.ibm.com/comm/research.nsf/pages/d.compsci.raviv.winner2008.html}
	\end{enumerate}
\item Computing Innovation Fellows (CIFellows); post my profile on \url{http://cifellows.org/profiles/}; also see \url{http://www.cifellows.org/}
\item Society for Industrial and Applied Mathematics: \vspace{-0.3cm}
	\begin{enumerate} \itemsep -2pt
	\item Job Search Resources for Students: \url{http://www.siam.org/careers/resources.php}
	\item SIAM Job Board: \url{http://jobs.siam.org/}
	\item Careers in the Math Sciences: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item \url{http://www.siam.org/careers/sinews.php}
		\item Has advice about: \vspace{-0.1cm}
			\begin{enumerate} \itemsep -1pt
			\item planning for my career (life after grad school)
			\item research careers in research institutes (and/or corporate research labs)
			\item seeking a junior academic position in the US
			\item obtaining/procuring reference letters
			\end{enumerate}
		\end{enumerate}
	\end{enumerate}
\item The European Mathematical Society: \vspace{-0.3cm}
	\begin{enumerate} \itemsep -2pt
	\item Open Positions: \url{http://www.euro-math-soc.eu/jobs.html}
	\end{enumerate}
\item Mathematical Optimization Society (MOS; formerly known as Mathematical Programming Society, MPS): \vspace{-0.3cm}
	\begin{enumerate} \itemsep -2pt
	\item Job Postings: \url{http://www.mathprog.org/?nav=links}
	\end{enumerate}
\item NSF Mathematical Sciences Institutes: \url{http://mathinstitutes.org/}
\end{enumerate}






%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Resources Concerning the Application for Junior Faculty Positions}
\label{resourcesforjnrprof}

Resources concerning the application for junior faculty positions: \vspace{-0.3cm}
\begin{enumerate} \itemsep -4pt
\item Computing Research Association (CRA): \vspace{-0.3cm}
	\begin{enumerate} \itemsep -2pt
	\item \url{http://www.cra.org/for-students/}
	\item CRA's Job Announcements: \url{http://www.cra.org/ads/}
	\item Computing Postdoc Job Opportunities: \url{http://cifellows.org/opportunities}
	\item Computing Postdoc Profiles: \url{http://cifellows.org/profiles}
	\item Mailing lists of the Computer Research Association's Committee on the Status of Women in Computing Research (CRA-W): \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item Subscribe to these and receive announcements concerning openings for junior faculty positions.
		\item \url{http://www.cra-w.org/mailinglists}
		\item \url{http://www.cra-w.org/PhdjobhuntHers}
		\end{enumerate}
	\end{enumerate}
\item American Association of University Professors: \vspace{-0.3cm}
	\begin{enumerate} \itemsep -2pt
	\item Career Center: \url{http://careercenter.aaup.org/search.cfm}
	\item Issues in Higher Education: \url{http://www.aaup.org/AAUP/issues/}
	\end{enumerate}
\item The Chronicle of Higher Education: \vspace{-0.3cm}
	\begin{enumerate} \itemsep -2pt
	\item Global Jobs: \url{http://chronicle.com/section/Global-Jobs/434/}
	\item Great Colleges to Work For: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item \url{http://chronicle.com/section/Great-Colleges-to-Work-For/156/}
		\item \url{http://chronicle.com/section/The-Academic-Workplace/156}
		\item \url{http://chronicle.com/article/Great-Colleges-to-Work-For/65724/}
		\end{enumerate}
	\item CV Doctor: \url{http://chronicle.com/article/The-CV-Doctor-Is-Back/49086/}
	\end{enumerate}
\item Nature Publishing Group (a division of Macmillan Publishers Limited): \vspace{-0.3cm}
	\begin{enumerate} \itemsep -2pt
	\item {\it naturejobs.com}: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item Jobs and careers: \url{http://www.nature.com/naturejobs/index.html}
		\item Career toolkit: \vspace{-0.1cm}
			\begin{enumerate} \itemsep -1pt
			\item \url{http://www.nature.com/naturejobs/career-toolkit/index.html}
			\item Salaries: \vspace{-0.1cm}
				\begin{itemize} \itemsep -1pt
				\item \url{http://www.nature.com/naturejobs/career-toolkit/salaries/index.html}
				\item Nature Publishing Group, ``Naturejobs international salary survey, 2010,'' in {\it naturejobs.com}: Career toolkit: Salaries: Salary survey, 2010. Available online at: \url{http://www.nature.com/naturejobs/salary/survey/2010/index.html}; last accessed on December 31, 2010.: \vspace{-0.1cm}
					\begin{itemize} \itemsep -1pt
					\item There are significant differences in the incomes of researchers between academia and industry in the U.S. and in Europe.
					\item Academics in Northern and Central Europe tend to make more than those in Southern Europe.
					\item Academics in the U.S. still dominate in terms of wages and benefits.
					\item There are less differences between the salaries of men and women in Southern Europe than the rest of Europe and the U.S..
					\end{itemize}
				\end{itemize}
			\item Podcasts: \vspace{-0.1cm}
				\begin{itemize} \itemsep -1pt
				\item Nature Publishing Group, ``Lecturer jobs,'' {\it naturejobs.com}: Career toolkit: Podcasts. Available online at: \url{http://media.nature.com/download/nature/podcast/naturejobs/naturejobs-2010-06-25.mp3}; last accessed on December 31, 2010. \vspace{-0.1cm}
					\begin{itemize} \itemsep -1pt
					\item Being a tenured/tenure-track professor involves spending about 20\% of my time on teaching, 10\% of my time on administrative activities, and the rest of my time (70\%) on research.
					\item Being a tenured/tenure-track or teaching professor involves: curricular design; and dealing with students from a broad spectrum of cultures and abilities (including students with disabilities and behavioral problems) -- undergraduates tend to start college in their late teens, and many of them are not sufficiently matured.
					\item The time spend on research would involve: managing a research lab; hiring students (undergraduates and grad students), postdocs, and technicians; and applying for funding.
					\item Two stages of getting tenure: 1) find a research topic/problem to work on, plan my research projects, broaden my social network of researchers so that I can collaborate with them or allow some members of the review committee for funding applications to get to know me, and be a co-instructor for graduate classes (\& possibly, lead the discussions/tutorials) and teach undergraduate classes; 2) write and submit research grant applications, \& start teaching classes as the primary instructor.
					\item Try to finish writing research papers based on my postdoctoral research projects prior to becoming a professor, so that I can start writing research grants based on my publications.
					\item Take note that my start-up fund as a junior professor may be low (say tens of thousands of dollars/Euro). This may prevent me from doing much research, unless only a small capital is needed to get my research started.
					\item When writing my grant proposal, specify and explain what would make my proposed technique stand out from the others.
					\item Give talks, including those in department seminars.
					\end{itemize}
				\end{itemize}
			\end{enumerate}
		\end{enumerate}
	\item Quirin Schiermeier, ``Graphic Detail: The real value of a scientist's wage,'' in {\it Nature}, Vol. 450, No. 7170, pp. 597, November 29, 2007. Available online at: \url{http://dx.doi.org/10.1038/450597a}; last accessed on December 31, 2010. [ ``Graphic Detail: The real value of a scientist's wage -- Researchers' spending power is not what it seems.'' ] \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item Salaries of academics in Switzerland are the highest, but Switzerland has the highest cost of living.
		\item Salaries in Northern and Central Europe are better than those in Southern Europe.
		\item Also, salaries in the US and Japan are comparable to those in Northern and Central Europe.
		\item Salaries in Israel are comparable to those in Southern Europe. E.g., they are comparable to those in France and Italy.
		\end{enumerate}
	\end{enumerate}
\item Times Higher Education (THE): \vspace{-0.3cm}
	\begin{enumerate} \itemsep -2pt
	\item Advanced Job Search: \url{http://www.timeshighereducation.co.uk/jobs_home.asp?navCode=84}
	\item Career: \url{http://www.timeshighereducation.co.uk/section.asp?navcode=96}
	\end{enumerate}
\item {\it Mathematical Association of America} (MAA): \vspace{-0.3cm}
	\begin{enumerate} \itemsep -2pt
	\item Information for new Ph.D.s seeking academic careers
	\item \url{http://www.maa.org/careers/}
	\item MAA Math Classifieds: \url{http://www.mathclassifieds.org/home/index.cfm?site_id=1925}
	\end{enumerate}
\item American Mathematical Society: \vspace{-0.3cm}
	\begin{enumerate} \itemsep -2pt
	\item Information on applying for positions in academia: \url{http://www.ams.org/programs/students/programs/students/gradinfo/gradinfo}
	\item \url{http://www.ams.org/profession/career-info/new-phds/new-phds}
	\end{enumerate}
\item Association for Women in Science (AWIS) career library: \url{http://www.awis.affiniscape.com/displaycommon.cfm?an=1&subarticlenbr=249}
\item American Psychological Association's resources for grad students and postdocs: \url{http://www.apa.org/education/grad/index.aspx}
\item {\it HigherEdJobs.com}: \url{http://www.higheredjobs.com/}
\item IEEE Real World Engineering Projects (RWEP): \vspace{-0.3cm}
	\begin{enumerate} \itemsep -2pt
	\item resources to help plan and run projects in EECS and related fields that will benefit humanity
	\item \url{http://www.realworldengineering.org/}
	\end{enumerate}
\item iBerry (collection of job lists): \url{http://iberry.com/cms/jobs.htm}
\item Common CV Network (for research and academic positions in Canada): \url{http://www.cvcommun.net/index_e.html}
\item University of Pennsylvania: \vspace{-0.3cm}
	\begin{enumerate} \itemsep -2pt
	\item Stephanie Weirich, {\it Computer Science Faculty Job Search Resources}, Department of Computer and Information Science, School of Engineering and Applied Science, University of Pennsylvania. Available at: \url{http://www.seas.upenn.edu/~sweirich/resources.htm}; last accessed on September 5, 2010.
	\end{enumerate}
\item {\tt Blue Lab Coats}, {\it Academic Job Applications}. Available at: \url{http://bluelabcoats.wordpress.com/application-pkgs/}; last accessed on September 10, 2010.
\item Inside Higher Ed: \url{http://www.insidehighered.com/career/seekers}
\item Advice on giving the job talk: \vspace{-0.3cm}
	\begin{enumerate} \itemsep -2pt
	\item John Farrell, ``What to Say in a Good Research Talk,'' Department of Computer Science, James Cook University, May 1994. Available at: \url{http://www.computersciencestudent.com/SS/HowTo/ResearchTalkJohnFarrell.html}; last accessed on August 25, 2010.
	\end{enumerate}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\item --- --- --- --- --- --- --- --- --- --- --- --- --- --- --- --- --- --- --- --- --- --- --- --- --- --- --- --- --- --- ---
% Residential Education
\item \colorbox{blue}{\bf Residential Education}: \vspace{-0.3cm}
	\begin{enumerate} \itemsep -2pt
	\item Telluride Association: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item Information about how to become a Faculty Fellow at the Cornell Branch and the Michigan Branch of Telluride Association, which are ``residential colleges'': \url{http://www.tellurideassociation.org/programs/college_faculty.html}
		\end{enumerate}
	\end{enumerate}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\item --- --- --- --- --- --- --- --- --- --- --- --- --- --- --- --- --- --- --- --- --- --- --- --- --- --- --- --- --- --- ---
% Awards, grants, and fellowships to look out for
\item \colorbox{blue}{\bf Awards, grants, and fellowships to look out for}: \vspace{-0.3cm}
	\begin{enumerate} \itemsep -2pt
	\item NSF Career Grant / NSF Career Award
	\item Heinz Family Philanthropies, The Heinz Awards: \url{http://www.heinzawards.net/awards}
	\item Sloan Research Fellowships; Alfred P. Sloan Foundation: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item Applicants must ``hold a Ph.D. (or equivalent) in chemistry, physics, mathematics, computer science, economics, neuroscience or computational and evolutionary molecular biology, or in a related interdisciplinary field''
		\item Applicants must be tenure-track junior faculty in a North American college or university
		\item \url{http://www.sloan.org/fellowships}
		\end{enumerate}
	\item Santa Fe Institute's Miller Distinguished Scholarship (for excellent interdisciplinary researchers): \url{http://www.santafe.edu/research/miller-scholars/}
	\item Lemelson-MIT Prize (for mid-career innovators): \url{http://web.mit.edu/invent/a-prize.html}
	\item Research Corporation for Science Advancement: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item Cottrell College Science Awards (for science researchers at predominantly undergraduate US colleges and universities): \url{http://www.rescorp.org/cottrell-college-science-awards}
		\item Cottrell Scholar Awards (for science researchers at US colleges and universities): \url{http://www.rescorp.org/cottrell-scholar-awards/}
		\end{enumerate}
	\item {\it Semiconductor Industry Association} University Researcher Awards: \url{http://www.sia-online.org/cs/papers_publications/press_release_detail?pressrelease.id=1722}
	\item Packard Fellowships for Science and Engineering (for professors at selected US universities): \url{http://www.packard.org/genericDetails.aspx?RootCatID=3&CategoryID=152}
	\item {\it American Society for Engineering Education} awards: \url{http://www.asee.org/activities/awards/division.cfm}
	\item Hellman Fellowship in Science and Technology Policy (for early-career professionals with training in science or engineering who are interested in transitioning to a career in public policy and administration): \url{http://www.amacad.org/hellman.aspx}
	\item Simons Foundation's {\it Collaboration Grants for Mathematicians}: \url{https://simonsfoundation.org/funding-guidelines/current-funding-opportunities/collaboration-grants-for-mathematicians}
	\item The National Science Foundation: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item Alan T. Waterman Award (for junior faculty in the US): \url{http://www.nsf.gov/od/waterman/waterman.jsp} 
		\end{enumerate}
	\item Computing Research Association (CRA): A. Nico Habermann Award, \url{http://www.cra.org/awards/habermann-current/}
	\item Microsoft New Faculty Fellowship Award: \url{http://research.microsoft.com/en-us/collaboration/awards/msrff_all.aspx#2005}
	\item Global Semiconductor Alliance (GSA): Dr. Morris Chang Exemplary Leadership Award
	\end{enumerate}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\item --- --- --- --- --- --- --- --- --- --- --- --- --- --- --- --- --- --- --- --- --- --- --- --- --- --- --- --- --- --- ---
% Underrepresented minority outreach
\item \colorbox{blue}{\bf Underrepresented minority outreach}: \vspace{-0.3cm}
	\begin{enumerate} \itemsep -2pt
	\item The Mathematical Association of America: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item Pre-College Programs: \url{http://www.maa.org/funding/pre_college.html}
		\item Programs for Undergraduate Students: \url{http://www.maa.org/funding/undergraduate.html}
		\item Special Interest Group of the MAA on Research in Undergraduate Mathematics Education (SIGMAA RUME): \url{http://sigmaa.maa.org/rume/}. Also, see \url{http://sigmaa.maa.org/rume/highlights.html}.
		\end{enumerate}
	\end{enumerate}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\item --- --- --- --- --- --- --- --- --- --- --- --- --- --- --- --- --- --- --- --- --- --- --- --- --- --- --- --- --- --- ---
% Resources for preparing the teaching statement, and developing a teaching philosophy and methodology
\item \colorbox{blue}{\bf Resources for preparing the teaching statement, and developing a teaching philosophy and methodology}: \vspace{-0.3cm}
	\begin{enumerate} \itemsep -2pt
	\item Missouri University of Science and Technology (formerly University of Missouri-Rolla): \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item Department of Electrical and Computer Engineering: \vspace{-0.1cm}
			\begin{enumerate} \itemsep -1pt
			\item Cp Eng 382 - Teaching Engineering (Summer 20XY): \vspace{-0.1cm}
				\begin{itemize} \itemsep -1pt
				\item \url{http://ece.mst.edu/documents/CpE_382.doc}
				\item Learn about: \vspace{-0.1cm}
					\begin{itemize} \itemsep -1pt
					\item teaching objectives and techniques
					\item knowledge taxonomies
					\item cognitive development
					\end{itemize}
				\item Learn how to: \vspace{-0.1cm}
					\begin{itemize} \itemsep -1pt
					\item use course objectives to design a course
					\item communicate using traditional and cutting-edge media, which includes making effective presentations via various communication modes, including traditional lecture, transparencies, and PowerPoint slides
					\item select textbook(s) and recommended books
					\item assess student learning
					\item grade/evaluate assignments, presentations, and projects in a way that addresses the psychological aspects of learning
					\item recognize and adapt to different student learning styles, 
					\item facilitate cooperative/active learning
					\item improve student discipline
					\end{itemize}
				\item Develop course content and student evaluation techniques to meet the elements of ABET criteria
				\item Critique evaluation methods including homework, exams, quizzes, reports/papers, and portfolios
				\item Learn to speak and/or write competently on educational hot topics, including collaborative learning, distance education, self-paced learning, web tools/educational software, and learning communities
				\item Develop course objectives
				\item Describe the parts of a syllabus, and prepare a syllabus
				\item Describe methods to prevent cheating
				\item Describe the elements of effective student advising at both the undergraduate and graduate levels
				\item List what makes one a good listener
				\item Prepare an academic application and identify the issues involved in the academic hire
				\item Describe appropriate responses to student situations such as death, depression, cheating, pregnancy, hugs
				\item Name sources of additional teaching training
				\end{itemize}
			\end{enumerate}
		\end{enumerate}
	\item Sergio Toral Marin, Mar{\'{i}}a del Roc{\'{i}}o Mart{\'{i}}nez-Torres, Federico Barrero, ``Reforming ICT Graduate Programs to Meet Professional Needs,'' {\it Computer}, vol. 43, no. 10, IEEE Computer Society Press, pp. 22-29, June 2010, DOI:10.1109/MC.2010.186.: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item To access this article, use its DOI Bookmark: \url{http://doi.ieeecomputersociety.org/10.1109/MC.2010.186} or \url{http://dx.doi.org/10.1109/MC.2010.186}.
		\item It discusses how ICT Masters degree programs in Europe can meet the needs and demands of the ICT industry and society. That is, it discusses how well European universities empower Masters students for jobs and careers in the ICT industry.
		\item Note that the definition and usage of ICT is non-standard among researchers of computer science and engineering higher education in the United States. Here, I am referring to researchers (mostly professors and Ph.D. students) who do research about:: \vspace{-0.1cm}
			\begin{enumerate} \itemsep -1pt
			\item the quality of computer science and engineering education;
			\item how well do these education programs empower computer science and engineering students to pursue the careers that they desire; and
			\item issues concerning the diversity of the student body and faculty in computer science and engineering.
			\end{enumerate}
		\item ICT is reasonably well-defined and used in Europe, and poorly defined and used elsewhere (especially in Asia).
		\item In American, programs related to the computing professions are: computer science; computer engineering; electrical engineering; and information systems. There may be more esoteric ``majors'' (as as ``gaming and animation''), but these majors don't usually have recommended frameworks and standards for their curriculum.
		\end{enumerate}
	\item ACM and IEEE Computer Society are professional organizations for the IT industry (and related industries, such as the semiconductor and electronic industries) that are leaders in helping educators plan and design their curriculum in computer science and engineering.: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item A gist of what computer science and computer engineering degree programs should empower students to have are listed in the short article on, ``Skills You'll Learn if You Study Computing''. Available online at: \url{http://computingcareers.acm.org/?page_id=15}; last accessed on November 22, 2010.
		\item Recommended computer science and computer engineering curricular can be found online at: \url{http://www.acm.org/education/curricula-recommendations} or \url{http://www.computer.org/portal/web/education/Curricula}; last accessed on November 22, 2010: \vspace{-0.1cm}
			\begin{enumerate} \itemsep -1pt
			\item As a Ph.D. student in computer science (or computer engineering), you should have most of the skills and knowledge specified in the recommended curricular for students in computer science (or computer engineering).
			\item You mostly probably need these skills and knowledge to pass your Ph.D. preliminary exam in a decent US CS Ph.D. program.
			\end{enumerate}
		\item ACM Special Interest Group on Computer Science Education (SIGCSE): \url{http://www.sigcse.org/}
		\item Association for Computing Machinery's Special Interest Group for Information Technology Education (SIGITE): \url{http://www.sigite.org/}
		\item ``Future of Computing Education Summit'': \url{http://www.acm.org/education/future-of-computing-education-summit}
		\end{enumerate}
	\item ABET, Inc. (formerly the Accreditation Board for Engineering and Technology): \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item ABET, {\it Download Accreditation Criteria and Forms}, 2010: \vspace{-0.1cm}
			\begin{enumerate} \itemsep -1pt
			\item \url{http://www.abet.org/forms.shtml}
			\item Look at the sections on ``student outcomes,'' and ``program criteria (including curriculum).''
			\item ABET Engineering Accreditation Commission, ``Criteria for Accrediting Engineering Programs: Effective for Evaluations During the 2011-2012 Accreditation Cycle,'' ABET, Baltimore, MD, October 30, 2010. Available online at: \url{http://www.abet.org/Linked%2520Documents-UPDATE/Program%2520Docs/abet-eac-criteria-2011-2012.pdf}; last accessed on November 22, 2010.
			\item ABET Engineering Accreditation Commission, ``Criteria for Accrediting Computing Programs: Effective for Evaluations During the 2011-2012 Accreditation Cycle,'' ABET, Baltimore, MD, October 30, 2010. Available online at: \url{http://www.abet.org/Linked%2520Documents-UPDATE/Program%2520Docs/abet-cac-criteria-2011-2012.pdf}; last accessed on November 22, 2010.
			\end{enumerate}
		\end{enumerate}
	\item American Institute of Mathematics: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item Resources for the Math Community: \vspace{-0.1cm}
			\begin{enumerate} \itemsep -1pt
			\item \url{http://www.aimath.org/mathcommunity/}
			\item David W. Farmer, ``The AIM REU: individual projects with a common theme,'' in the {\it Proceedings of the Conference on Promoting Undergraduate Research in Mathematics}, American Mathematical Society, 2006. Available online at: \url{http://www.aimath.org/mathcommunity/farmerREU.pdf}; last accessed on January 9, 2010. [ ``AIM Research Experience for Undergraduates (REU)'' ]
			\item Sally Koutsoliotas and David W. Farmer, ``Preparing students to give talks,'' American Institute of Mathematics. Available online at: \url{http://www.aimath.org/mathcommunity/studenttalks.pdf}; last accessed on January 9, 2010. [ ``Preparing students to give talks'' ]
			\end{enumerate}
		\end{enumerate}
	\end{enumerate}
\end{enumerate}











%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Grad School Information}
\label{gradschinfo}

Things for me to look into when considering graduate and professional programs: \vspace{-0.3cm}
\begin{enumerate} \itemsep -4pt
\item Is the graduate or professional program accredited?
\item Would attending the graduate/professional program help me obtain my career goals?
\item Would attending the graduate/professional program help me obtain my career goals?
\item See \url{http://gradschool.princeton.edu/facts/time_to_degree/naturalsciences/} for statistics of graduates from various programs at Princeton University.
\item Some statistics that you may wanna look into include, average number of Ph.D. students per Ph.D. advisor (tells you about advisor-to-advisee ratios), number of Ph.D. graduates for the Ph.D. program per year (tells you about the size of the department), graduate outcomes (what did alumni do after their Ph.D. programs), drop-out rate, failure rate for Ph.D. preliminary and qualifying examinations, and reasons for dropping out of the Ph.D. program.
\item Some research labs do list the names of alumni members (Ph.D. and Masters students, undergraduates, and postdocs). They may also include their first vocation after their Ph.D. program, and what are they currently doing. You can use this to help you gauge the strengths/weaknesses of the lab/advisor.
\item Accommodation options. Is it hard to find housing in the surrounding area? Is housing in the surrounding area cheap? What are some of the statistics of the local population? LA Times has some statistics of local populations in LA. You can determine the average income, highest level of education, political views, and so on... Try to determine if there is an equivalent of that for the local area.
\item 
\end{enumerate}


Grad school info: \vspace{-0.3cm}
\begin{itemize} \itemsep -4pt
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\item general information and advice about grad school: \vspace{-0.3cm}
	\begin{enumerate} \itemsep -2pt
	\item IEEE: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item Susan Karlin, ``How to Choose A Grad School: Figure out what you want and who can give it to you,'' {\it IEEE Spectrum}, September 2005. Available at: \url{http://spectrum.ieee.org/at-work/education/how-to-choose-a-grad-school}; last accessed on August 28, 2010.
		\item IEEE Potentials, Volume 21, Issue 3, Aug/Sep 2002.
		\item IEEE Potentials, Volume 24, Issue 3, Aug/Sep 2005.
		\end{enumerate}
	\item ACM: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item ACM, {\it ACM Crossroads Student Resources}, ACM, New York, NY, Aug 17, 2005. Available at: \url{http://oldwww.acm.org/crossroads/resources/}; last accessed on August 29, 2010.
		\item ACM, {\it Graduate Educational Resources from ACM Crossroads}, ACM, New York, NY, Aug 7, 2005. Available at: \url{http://oldwww.acm.org/crossroads/resources/graduate.html}; last accessed on August 29, 2010.
% http://oldwww.acm.org/crossroads/resources/graduate.html
		\item {\it ACM Crossroads} articles on grad school application and life in grad school: \cite{Agre1997,desJardins1994,desJardins1995,desJardins2001,desJardins2008,Pottinger1999,Wendler2010}.	
		\end{enumerate}
	\item European Commission: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item Marie Curie Actions: \url{http://ec.europa.eu/research/mariecurieactions/index.htm}... {\bf \color{blue} SCHOLARSHIPS!!!}
		\item {\it EURAXESS} Research Job Vacancies: \url{http://ec.europa.eu/euraxess/index.cfm/jobs/jvSearch} or \url{http://ec.europa.eu/euraxess/index_en.cfm?l1=13&l2=3&initSearch=1#}... {\bf \color{blue} SCHOLARSHIPS!!!}
		\item European Commission, ``Third European Report on Science \& Technology Indicators 2003,'' Directorate-General for Research, European Commission. Available at: \url{http://cordis.europa.eu/indicators/contacts.htm}; last accessed on September 1, 2010. Report on European universities and research initiatives.
		\item Publications by the Directorate-General for Research, European Commission, about research initiatives and output in Europe: \url{http://cordis.europa.eu/indicators/publications.htm}
		\end{enumerate}
	\item American Psychological Association: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item American Psychological Association, {\it gradPSYCH} [ magazine ], American Psychological Association, Washington, DC. Available at: \url{http://www.apa.org/gradpsych/}; last accessed on September 1, 2010. [ Read issues from May 2003 till January 2005; {\color{blue} \bf This is an excellence source of information about doing well in graduate school and internships, and seeking research careers in academia and the industry.} ]
		\end{enumerate}
	\item Computing Research Association (CRA): \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item Information for Undergraduate and Graduate Students: \url{http://www.cra.org/for-students/}
		\item Computer Research Association's Committee on the Status of Women in Computing Research (CRA-W), ``Graduate Student Information Guide''. Available at: \url{http://www.cra-w.org/sites/default/files/grad-guide.pdf}; CRA-W $\Rightarrow$ Resources $\Rightarrow$ Publications $\Rightarrow$ link and description to the guide, ``Graduate Student Information Guide''; last accessed on September 3, 2010.
		\end{enumerate}
	\item American Mathematical Society: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item {\it Applying to Graduate School}. Available at: \url{http://www.ams.org/profession/career-info/grad-school/grad-school}; last accessed on September 2, 2010.
		\end{enumerate}
	\item The Mathematical Association of America: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item {\it MAA Students}. Available at: \url{http://www.maa.org/students/}; last accessed on September 2, 2010.
		\end{enumerate}
	\item American Institute of Mathematics: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item Resources for the Math Community: \vspace{-0.1cm}
			\begin{enumerate} \itemsep -1pt
			\item \url{http://www.aimath.org/mathcommunity/}
			\item David W. Farmer, ``The AIM REU: individual projects with a common theme,'' in the {\it Proceedings of the Conference on Promoting Undergraduate Research in Mathematics}, American Mathematical Society, 2006. Available online at: \url{http://www.aimath.org/mathcommunity/farmerREU.pdf}; last accessed on January 9, 2010. [ ``AIM Research Experience for Undergraduates (REU)'' ]
			\item Sally Koutsoliotas and David W. Farmer, ``Preparing students to give talks,'' American Institute of Mathematics. Available online at: \url{http://www.aimath.org/mathcommunity/studenttalks.pdf}; last accessed on January 9, 2010. [ ``Preparing students to give talks'' ]
			\end{enumerate}
		\end{enumerate}
	\item University of California, Berkeley: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item Matthew Moskewicz, Parallel Computing Laboratory (Par Lab), Department of Electrical Engineering and Computer Sciences: \vspace{-0.1cm}
			\begin{enumerate} \itemsep -1pt
			\item Developed the {\it Chaff} SAT solver with Conor Madigan as undergrads that is 10-100X faster than then existing SAT solvers.
			\item He is named a co-winner of the 2009 CAV Award, along with his co-developers of {\it Chaff} and the developers of the {\it GRASP} SAT solver, for his fundamental contribution to the field of Computer Aided Verification.
			\item \url{http://www.princeton.edu/engineering/eqnews/spring01/feature5.html}
			\item \url{http://parlab.eecs.berkeley.edu/people/matthew-moskewicz}
			\end{enumerate}
		\item Mark Borgschulte, ``Economics Grad School Application Advice,'' Department of Economics, University of California, Berkeley. Available online at: \url{http://sites.google.com/site/markborgschulte/economicsgradschoolapplicationadvice}; last accessed on January 9, 2010.
		\item Mark Borgschulte, ``Info for Berkeley Admits,'' Department of Economics, University of California, Berkeley. Available online at: \url{http://sites.google.com/site/markborgschulte/infoforberkeleyadmits}; last accessed on January 9, 2010.
		\item Mark Borgschulte, ``Reading List,'' Department of Economics, University of California, Berkeley. Available online at: \url{http://sites.google.com/site/markborgschulte/readinglist}; last accessed on January 9, 2010.
		\item {\it Secret Blogging Seminar} is a blog written by recent Ph.D. graduates from Berkeley's Department of Mathematics. Noah Snyder, ``Thoughts on graduate school,'' May 13, 2009. Available at: \url{http://sbseminar.wordpress.com/2009/05/13/thoughts-on-graduate-school/}; last accessed on September 1, 2010.
		\item {\it UC Berkeley Career Center}, ``Graduate School - Letters of Recommendation,'' UC Berkeley. Available at: \url{https://career.berkeley.edu/grad/gradletter.stm}; last accessed on September 5, 2010.
		\end{enumerate}
	\item Carnegie Mellon University, Computer Science Department: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item Carnegie Mellon University, {\it Ph.D. in Computer Science}, Computer Science Department, Carnegie Mellon University. Available at: \url{http://www.csd.cs.cmu.edu/education/phd/index.html}; last accessed on August 28, 2010.
		\item Mark Leone, {\it Advice on Research and Writing}, Computer Science Department, Carnegie Mellon University. Available at: \url{http://www-2.cs.cmu.edu/afs/cs.cmu.edu/user/mleone/web/how-to.html}; last accessed on August 28, 2010. Also, see \url{http://www.cs.cmu.edu/~mleone/how-to.html} for another copy. [Mark Leone has graduated with a MS CS from CMU.]
		\item Jason I. Hong, {\it Grad School Advice}, Human Computer Interaction Institute, School of Computer Science, Carnegie Mellon University, Sept 20, 2006. Available online at: \url{http://www.cs.cmu.edu/~jasonh/advice.html}; last accessed on December 17, 2010.
		\item women@SCS School of Computer Science: \vspace{-0.1cm}
			\begin{enumerate} \itemsep -1pt
			\item Career Advice: \url{http://women.cs.cmu.edu/Resources/JobsResearch/careeradvice.php}
			\end{enumerate}
		\end{enumerate}
	\item University of California, San Diego: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item UCSD VLSI CAD Laboratory, {\it Useful tips on how to succeed in graduate school and your subsequent research career}, Department of Computer Science and Engineering \& Department of Electrical and Computer Engineering, University of California, San Diego. Available at: \url{http://vlsicad.ucsd.edu/Research/Advice/index.html}; last accessed on August 28, 2010. \colorbox{yellow}{\bf EXCELLENT!!!}
		\item Mihir Bellare, ``The Ph.D Experience,'' Department of Computer Science \& Engineering, University of California at San Diego. Available at: \url{http://cseweb.ucsd.edu/~mihir/phd.html}; last accessed on September 13, 2010. [ See {\it Educational} material about graduate school, research, and technical writing at: \url{http://cseweb.ucsd.edu/users/mihir/education.html}. ]
		\item Fan Chung Graham, ``A few words on research for graduate students (especially for those potential combinatorialists),'' in {\it Teaching}, Department of Mathematics, University of California, San Diego. Available online at: \url{http://math.ucsd.edu/~fan/teach/gradpol.html}; last accessed on January 9, 2010.
		\end{enumerate}
	\item University of Michigan, Ann Arbor: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item  Igor Markov, Department of Electrical Engineering and Computer Science: \url{http://www.eecs.umich.edu/~imarkov/i_students.html}. In particular, see his ``Advice for graduate students''.
		\end{enumerate}
	\item University of California, Los Angeles: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item Philip E. Agre, ``Advice for Undergraduates Considering Graduate School,'' UCLA Department of Information Studies, University of California, Los Angeles, October 1996 (Modified: May 2001). Available at: \url{http://polaris.gseis.ucla.edu/pagre/grad-school.html}; last accessed on August 28, 2010. See \url{http://polaris.gseis.ucla.edu/pagre/grad-school.pdf} for a PDF copy of this article. \colorbox{yellow}{\bf CLASSIC!!!}. See \url{http://polaris.gseis.ucla.edu/pagre/index.html} for more articles.
		\item Terence Tao, {\it Career advice}, Department of Mathematics, University of California, Los Angeles. Available at: \url{http://terrytao.wordpress.com/career-advice/}; last accessed on September 1, 2010. Additional information can be found at: \url{http://www.math.ucla.edu/~tao/}.
		\item Yu Hu: \vspace{-0.1cm}
			\begin{enumerate} \itemsep -1pt
			\item Yu Hu, ``Links: Programming Tools and Tips; and Documentation and Presentation,'' Electrical Engineering Department, University of California, Los Angeles, Aug 27, 2007. Available online at: \url{http://www.ee.ucla.edu/~hu/links.htm}; last accessed on September 18, 2010. [ This web page has resources for computer programming, and creating presentation slides and documentations. ]
			\item Courses @ UCLA, April 22, 2006: \url{http://www.ee.ucla.edu/~hu/course.htm}
			\item Research: \url{http://www.ee.ucla.edu/~hu/project.htm}
			\end{enumerate}
		\end{enumerate}
	\item Stanford University: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item John Ousterhout, ``My Favorite Sayings,'' Department of Computer Science, Stanford University, September 09, 2009. Available at: \url{http://www.stanford.edu/~ouster/cgi-bin/sayings.php}; last accessed on September 4, 2010. [Also, see {\it Odds \& Ends}: \url{http://www.stanford.edu/~ouster/cgi-bin/misc.php} ]
		\item Jeffrey Michael Heer, Department of Computer Science: \vspace{-0.1cm}
			\begin{enumerate} \itemsep -1pt
			\item The only Ph.D. student to have ever won the Microsoft Graduate Fellowship and the IBM Ph.D. Fellowship concurrently. After he won these fellowships as a Ph.D. student at Berkeley, IBM changed the rules for its Ph.D. fellowship so that nobody else can do this anymore. This prevents other companies from competing with IBM for hiring these fellows as research interns.
			\item \url{http://hci.stanford.edu/jheer/cv/}
			\end{enumerate}
		\item Ravi Vakil, ``For potential students,'' Department of Mathematics, Stanford University. Available at: \url{http://math.stanford.edu/~vakil/potentialstudents.html}; last accessed on September 1, 2010. [ ``Great articles and books'' in mathematics: \url{http://math.stanford.edu/~vakil/greatwriting.html}. Information about getting/writing letters of recommendation: \url{http://math.stanford.edu/~vakil/recommendations.html}. ]
		\item Philip Guo, {\it Academic Home Page}, Department of Computer Science, Stanford University. Available at: \url{http://www.stanford.edu/~pgbovine/academic.htm}; last accessed on September 1, 2010. [ See resources at the bottom of the page. Also, see \url{http://www.stanford.edu/~pgbovine/writings.htm} for his non-academic/research articles. ]
		\item Stanford University, {\it Tomorrow's Professor$^{\rm SM}$ Mailing List Links}, Center for Teaching and Learning, Stanford University. Available at: \url{http://www.stanford.edu/dept/CTL/Tomprof/links.html}; last accessed on September 1, 2010.
		\item Eran Magen, {\it How I Got Into the Stanford Psychology Ph.D. Program}, Department of Psychology, Stanford University. Available at: \url{http://www.howigotintostanford.com/}; last accessed on September 1, 2010.
		\item Stanford University, {\it Tutoring and Academic Support}, [Office of the] Vice Provost for Undergraduate Education, Stanford University. Available at: \url{http://ual.stanford.edu./ARS/index.html}; last accessed on September 1, 2010.
		\item Stanford University, ``Guidelines for Advising Relationships between Faculty Advisors and Graduate Students,'' Office of the Vice Provost for Graduate Education (VPGE), Stanford University, 2009. Available online at: \url{http://vpge.stanford.edu/docs/Advisor_Guidelines.pdf}; last accessed on December 22, 2010.
		\end{enumerate}
	\item University of Washington: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item University of Washington, {\it 10-Year Review Self-Study}, Department of Computer Science \& Engineering, University of Washington, January 2000. Available at: \url{http://www.cs.washington.edu/homes/lazowska/selfstudy/}; last accessed on September 2, 2010. See other information on Prof. Ed Lazowska's web page: \url{http://www.cs.washington.edu/homes/lazowska/}.
		\item Yuriy Brun, {\it Yuriy Brun's Advice}, Department of Computer Science \& Engineering, University of Washington. Available at: \url{http://www.cs.washington.edu/homes/brun/advice/}; last accessed on August 28, 2010. See \url{http://www.cs.washington.edu/homes/brun/advice/PhDAdvice.pdf} for: Yuriy Brun, ``Getting a Ph.D. at the University of Southern California,'' May 20, 2010.
		\item Michael Ernst, {\it Advice for researchers and students}, Department of Computer Science \& Engineering, University of Washington. Available at: \url{http://www.cs.washington.edu/homes/mernst/advice/}; last accessed on August 28, 2010.
		\item Karin Strauss, {\it For graduate students} [ see the links on the left side of her home page ]. Available at: \url{http://www.cs.washington.edu/homes/kstrauss/}; last accessed on September 3, 2010.
		\item Wanda Pratt, {\it Advice}, Information School \& Division of Biomedical \& Health Informatics / Department of Medical Education and Biomedical Informatics / School of Medicine, University of Washington. Available at: \url{http://faculty.washington.edu/wpratt/advice.htm}; last accessed on September 3, 2010.
		\item William A. Stein, {\it Home Page}, Department of Mathematics, University of Washington. Available at: \url{http://wstein.org/}; last accessed on September 5, 2010. {\bf \color{blue} [ Has GREAT resources for junior faculty application and research grant proposals. He has provided tar balls (or zip files) and PDF files of these material. ]}
		\item University of Washington Graduate School, {\it Re-envisioning the Ph.D. project}, University of Washington Graduate School, University of Washington. Available at: \url{http://www.grad.washington.edu/envision/index.html}; last accessed on August 28, 2010. [This research is about issues concerning Ph.D. programs, such as: how to improve the quality of Ph.D. programs and student outcomes, and the lifestyle (including social life) of Ph.D. students; and funding issues.]
		\end{enumerate}
	\item Duke University: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item Xiaowei Yang, {\it Advice Collection}, Department of Computer Science, Duke University. Available at: \url{http://www.cs.duke.edu/~xwy/advices.html}; last accessed on August 28, 2010.
		\end{enumerate}
	\item Columbia University: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item Department of Economics: \vspace{-0.1cm}
			\begin{enumerate} \itemsep -1pt
			\item Donald R. Davis, ``Ph.D. Thesis Research: Where do I Start?'', Department of Economics, Columbia University, February 2001. Available online at: \url{http://www.columbia.edu/~drd28/Thesis%20Research.pdf}; last accessed on January 9, 2010.
			\end{enumerate}
		\end{enumerate}
	\item Princeton University: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item Boaz Barak, Department of Computer Science: \vspace{-0.1cm}
			\begin{enumerate} \itemsep -1pt
			\item He won the ACM Doctoral Dissertation Award.
			\item \url{http://awards.acm.org/doctoral_dissertation/}
			\item \url{http://www.cs.princeton.edu/~boaz/}
			\end{enumerate}
		\end{enumerate}
	\item The University of Texas at Austin: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item Department of Computer Science: \vspace{-0.1cm}
			\begin{enumerate} \itemsep -1pt
			\item Mike Dahlin, ``Advice to systems researchers,'' Department of Computer Science, The University of Texas at Austin. Available online at: \url{http://www.cs.utexas.edu/users/dahlin/advice.html}; last accessed on January 9, 2010.
			\end{enumerate}
		\end{enumerate}
	\item University of Pennsylvania: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item Stephanie Weirich, {\it Advice for Graduate Studies}, Department of Computer and Information Science, School of Engineering and Applied Science, University of Pennsylvania. Available at: \url{http://www.seas.upenn.edu/~sweirich/phdadvice.htm}; last accessed on September 5, 2010.
		\end{enumerate}
	\item Northwestern University: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item Department of Electrical Engineering and Computer Science; Robert R. McCormick School of Engineering and Applied Science: \vspace{-0.1cm}
			\begin{enumerate} \itemsep -1pt
			\item Lance Fortnow and William Gasarch, ``Graduate Student Guide,'' in their blog {\it Computational Complexity}, Department of Electrical Engineering and Computer Science, Robert R. McCormick School of Engineering and Applied Science, Northwestern University, February 21, 2007. Available at: \url{http://blog.computationalcomplexity.org/2007/02/graduate-student-guide.html}; last accessed on September 14, 2010. [ William Gasarch is from the Department of Computer Science at the University of Maryland, College Park. THIS IS EXCELLENT!!! ]
			\end{enumerate}
		\end{enumerate}
	\item Purdue University: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item Douglas E. Comer, {\it A few essays about Computer Science}, Department of Computer Science, Purdue University: \vspace{-0.1cm}
			\begin{enumerate} \itemsep -1pt
			\item \url{http://www.cs.purdue.edu/homes/dec/}
			\item Look for the section, ``A few essays about Computer Science''. The essay, ``How to generate a CS research topic,'' is funny: \url{http://www.cs.purdue.edu/homes/dec/essay.topic.generator.html}.
			\item Douglas E. Comer, ``Notes On The PhD Degree,'' Department of Computer Science, Purdue University. Available at: \url{http://www.cs.purdue.edu/homes/dec/essay.phd.html}; last accessed on September 12, 2010.
			\end{enumerate}
		\item Jan Vitek, {\it Home Page: Miscellaneous}, Department of Computer Science, Purdue University. Available online at: \url{http://www.cs.purdue.edu/homes/jv/}; last accessed on September 28, 2010.
		\end{enumerate}
	\item Cornell University: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item CU-ADVANCE Center (research and resource center concerning diversity and gender equity): \url{http://advance.cornell.edu/}
		\item Department of Computer Science, Faculty of Computing and Information Science (CIS): \vspace{-0.1cm}
			\begin{enumerate} \itemsep -1pt
			\item Charles F. Van Loan: \url{http://www.cs.cornell.edu/cv/default.htm}
			\end{enumerate}
		\end{enumerate}
	\item Rice University: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item Richard G. Baraniuk, ``Seven Steps to Success in Graduate School (and Beyond),'' Department of Electrical and Computer Engineering, George R. Brown School of Engineering, Rice University. Available online at: \url{http://www.ece.rice.edu/~richb/success.html}; last accessed on January 9, 2010.
		\end{enumerate}
	\item Yale University: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item Stephen C. Stearns, ``Some Modest Advice for Graduate Students,'' Department of Ecology and Evolutionary Biology, Yale University. Available at: \url{http://www.yale.edu/eeb/stearns/advice.htm}; last accessed on August 28, 2010.
		\item Stephen C. Stearns, ``Designs for Learning,'' Department of Ecology and Evolutionary Biology, Yale University. Available at: \url{http://www.yale.edu/eeb/stearns/designs.htm}; last accessed on August 28, 2010.
		\end{enumerate}
	\item Harvard University: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item H. T. Kung, ``Useful Things to Know About Ph. D. Thesis Research,'' Harvard School of Engineering and Applied Sciences, Harvard University. (Prepared for ``What is Research'' Immigration Course, Computer Science Department, Carnegie Mellon University, 14 October 1987)
		\item Susan Athey, ``Advice for Applying to Grad School in Economics,'' Department of Economics, Harvard University. Available online at: \url{http://kuznets.fas.harvard.edu/~athey/gradadv.html}; last accessed on January 9, 2010. Prof. Athey has also provided an article, ``Negotiating Senior Job Offers,'' on her web page; this would concern senior faculty job offers.
		\item The Collaborative on Academic Careers in Higher Education, Harvard University Graduate School of Education: \url{http://isites.harvard.edu/icb/icb.do?keyword=coache&tabgroupid=icb.tabgroup104863}
		\end{enumerate}
	\item University of Wisconsin-Madison: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item Department of Electrical and Computer Engineering; College of Engineering: \vspace{-0.1cm}
			\begin{enumerate} \itemsep -1pt
			\item Azadeh Davoodi: \url{http://homepages.cae.wisc.edu/~adavoodi/Links.htm}
			\end{enumerate}
		\item Dorothea Salo, {\it A Tale of Graduate School Burnout}. Available at: \url{http://members.terracom.net/~dorothea/gradsch/index.html}; last accessed on August 28, 2010.
		\item Dorothea Salo, {\it Straight Talk about Graduate School}. Available at: \url{http://members.terracom.net/~dorothea/gradsch/straighttalk.html}; last accessed on August 28, 2010.
		\item Dorothea Salo, {\it What to do before applying to graduate school}. Available at: \url{http://members.terracom.net/~dorothea/gradsch/success.html}; last accessed on August 28, 2010.
		\end{enumerate}
	\item Pennsylvania State University: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item Tao Xie and Yuan Xie, {\it Advice Collection}, Department of Computer Science at North Carolina State University, and Department of Computer Science and Engineering at Pennsylvania State University. Available at: \url{http://www.cse.psu.edu/~yuanxie/advice.htm}; last accessed on August 25, 2010. Also, see \url{http://people.engr.ncsu.edu/txie/advice/index.html} and \url{http://people.engr.ncsu.edu/txie/advice.htm}.
		\item Office of Engineering Diversity; Penn State College of Engineering: \vspace{-0.1cm}
			\begin{enumerate} \itemsep -1pt
			\item Office of Engineering Diversity, ``Tips for Graduate Students,'' Penn State College of Engineering, Pennsylvania State University, 2009. Available online at: \url{http://www.engr.psu.edu/mep/tips.html}; last accessed on December 9, 2010.: \vspace{-0.1cm}
				\begin{itemize} \itemsep -1pt
				\item Getting the most out of the relationship with your research advisor or boss: \vspace{-0.1cm}
					\begin{itemize} \itemsep -1pt
					\item {\bf Meet regularly} - you should insist on meeting once a week or at least every other week because it gives you motivation to make regular progress and it keeps your advisor aware of your work.
					\item {\bf Prepare for your meetings} - come to each meeting with: List of topics to discuss; Plan for what you hope to get out of the meeting; Summary of you have done since your last meeting; List of any upcoming deadlines; \& Notes from your previous meeting
					\item {\bf Email him/her a brief summary of EVERY meeting} - this helps avoid misunderstandings and provides a great record of your research progress. Include (where applicable): Time and plan for next meeting; New summary of what you think you are doing; To do list for yourself; To do list for your advisor; List of related work to read; List of major topics discussed; List of what you agreed on; \& List of advice that you may not follow
					\item {\bf Show your advisor the results of your work as soon as possible} - this will help your advisor understand your research and identify potential points of conflict early in the process. Summaries of related work. Anything you write about your research. Experimental results.
					\item {\bf Communicate clearly} - if you disagree with your advisor, state your objections or concerns clearly and calmly. If you feel something about your relationship is not working well, discuss it with him or her. Whenever possible, suggest steps they could take to address your concerns.
					\item {\bf Take the initiative} - you do not need to clear every activity with your advisor. He/she has a lot of work to do too. You must be responsible for your own research ideas and progress.
					\end{itemize}
				\item Getting the most out of what you read: \vspace{-0.1cm}
					\begin{itemize} \itemsep -1pt
					\item {\bf Be organized}. Keep an electronic bibliography with notes \& pointers to the paper files. Keep and file all the papers you have read or skimmed.
					\item {\bf Be efficient} - only read what you need to. Start by reading only the conclusion, scanning figures \& tables, and looking at their references. Read the other sections only if the paper seems relevant or you think it may help you get a different perspective. Skip the sections that you already understand (often the background and motivation sections).
					\item {\bf Take notes on every paper you find worth reading} - What problem are they trying to solve? What is their approach? How is it different from other approaches?
					\item {\bf Summarize what you have read on each topic} -- after you have read several papers covering some topic, note the: key problems; various formulations of the problem they are addressing; relationship among the various approaches; and alternative approaches
					\item {\bf Read Ph.D. theses} -- even though they are long they can be very helpful in quickly learning about what has been done is some field. Especially focus on: Background sections; Method sections; and Your advisor's thesis (this will give you an idea for what he/she expects from you).
					\end{itemize}
				\item Making continual progress on your research: \vspace{-0.1cm}
					\begin{itemize} \itemsep -1pt
					\item {\bf Keep a journal of your ideas} - write down everything you are thinking about even if you think it is stupid. It will help you keep track of your progress and keep you from going in circles. Do not plan to share it with anyone, so you can write freely.
					\item {\bf Set some reasonable goals with deadlines}: Identify key tasks that need to be completed; Set a reasonable date for completing them (on the order of weeks or months); Share this with your advisor or enlist your advisors help in creating the goals and deadlines; and Set some deadlines that you must keep (e.g., volunteer to give a student seminar on your research, work toward a conference paper submission deadline, etc.)
					\item {\bf Keep a to do list} - Checking off things on a to do list can feel very rewarding when you are working on a long-term project. List the small tasks that can be done in about an hour. Pick at least one that has to be completed each day.
					\item {\bf Continually update your: Problem statement}, Goals, Approach (or a list of possible approaches); One-minute version of your research (aka the elevator ride summary); and Five-minute version of your research
					\item {\bf Discuss your research with anyone who will listen} - use your fellow students, friends, family, etc. to practice discussing your research on various levels. They may have useful insights or you may find that verbalizing your ideas clarifies them for yourself.
					\item {\bf Write about your work}. Early stage: Write short idea papers and share them with your advisor and colleagues. Intermediate stage: Find workshops and conferences for submitting preliminary results. This can also help you set deadlines. Advanced stage: Target relevant journals.
					\item {\bf Avoid distractions} - it is easy to ignore your research in favor of more structured tasks such as taking classes, teaching classes, organizing student activities, creating web pages like this, etc. Minimize these kinds of activities or commitments.
					\item {\bf Confront your fears and weaknesses}: If you are afraid of public speaking, volunteer to give lots of talks. If you are afraid your ideas are stupid, discuss them with someone. If you are afraid of writing, write something about your research every day. One-minute version of your research (aka the elevator ride summary). Five-minute version of your research. List of advice that you may not follow.
					\item {\bf Balance reading, thinking, writing and hacking} - often research needs to be an iterative process across all of those tasks.
					\item {\bf Finding a thesis topic or formulating a research plan}. Pick something you find interesting - if you work on something solely because your advisor wants you to, it will be difficult to stay motivated ... Pick something your advisor finds interesting - if your advisor doesn't find it interesting he/she is unlikely to devote much time to your research. He/she will be even more motivated to help you if your project is on their critical path (although this has down sides too! )... Pick something the research community will find interesting - if you want to make yourself marketable... Make sure it addresses a real problem. Remember that your topic will evolve as you work on it. Pick something that is narrow enough that it can be done in a reasonable time frame. Have realistic expectations (i.e. Don't expect the Nobel Prize ). Don't worry that you will be stuck in this area for the rest of your career. It is very likely that you will be doing very different research after you graduate.
					\end{itemize}
				\item Characteristics to look for in a good advisor, mentor, boss, or committee member: \vspace{-0.1cm}
					\begin{itemize} \itemsep -1pt
					\item It is unreasonable to expect one person to have all of the qualities you desire. You should choose thesis committee members who are strong in the areas where your advisor is weak.
					\item {\bf Willing to meet with you regularly (about 1 hour every week or every other week). You can trust him/her to}: Give you credit for the work you do; Defend your work when you are not around; Tell you when your work is or is not good enough; Help you graduate in a reasonable time frame; and Look out for you professionally and personally
					\item {\bf Is interested in your topic. Has good personal and communication skills}: You can talk freely and easily about research ideas; Tells you when you are doing something stupid; Patient, Never feels threatened by your capabilities; Helps motivate you and keep you unstuck
					\end{itemize}
				\item {\bf Has good technical skills}. Can provide constructive criticism of papers you write or talks you give. Knows if what you are doing is good enough for a good thesis. Can help you figure out what you are not doing well; Can help you improve your skills; Can suggest related articles to read or people to talk to; Can tell you or help you discover if what you are doing has already been done; Can help you set and obtain reasonable goals. Will be around until you finish. Is well respected in his/her field. Has good connections for the type of job you would want when you graduate; Willing and able to provide financial and computing support.
				\item {\bf Avoiding the research blues}: \vspace{-0.1cm}
					\begin{itemize} \itemsep -1pt
					\item When you meet your goals, reward yourself.
					\item Don't compare yourself to senior researchers who have many more years of work and publications.
					\item Don't be afraid to leave part of your research problem for future work.
					\item Exercise.
					\item Use the student counseling services
					\item Occasionally, do something fun without feeling guilty! 
					\end{itemize}
				\end{itemize}
			\end{enumerate}
		\end{enumerate}
	\item Technion - Israel Institute of Technology: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item Department of Computer Science: \vspace{-0.1cm}
			\begin{enumerate} \itemsep -1pt
			\item 
			\end{enumerate}
		\end{enumerate}
	\item University of California, Santa Cruz: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item Department of Computer Science; Jack Baskin School of Engineering: \vspace{-0.1cm}
			\begin{enumerate} \itemsep -1pt
			\item CMPS/CMPE 200 - Research and Teaching in Computer Science and Engineering (and Applied Math and Statistics and Technology and Information Management) (Fall 2010) by Prof. Cormac Flanagan and Prof. Jose Renau (\& Prof. Alexandre Brandwajn???). Available online at: \url{http://www.soe.ucsc.edu/classes/cmps200/Fall10/}; last accessed on December 17, 2010. [ Also, see {\it CMPS 200 - Research and Teaching in Computer Science and Engineering}: \url{http://www.cs.ucsc.edu/courses/course?cmps200} ]
			\end{enumerate}
		\end{enumerate}
	\item The University of North Carolina at Chapel Hill: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item Ronald T. Azuma, {``So long, and thanks for the Ph.D.!'' a.k.a. ``Everything I wanted to know about C.S. graduate school at the beginning but didn't learn until later.'' The 4th guide in the Hitchhiker's guide trilogy (and if that doesn't make sense, you obviously have not read Douglas Adams}, v. 1.08, Department of Computer Science, The University of North Carolina at Chapel Hill, January 2003. Available at: \url{http://www.cs.unc.edu/~azuma/hitch4.html}; last accessed on September 3, 2010. [ Also, see {\it Guides to surviving Computer Science graduate school} at: \url{http://www.cs.unc.edu/~azuma/azuma_guides.html}. ]
		\end{enumerate}
	\item Johns Hopkins University: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item Adam Ruben, Department of Biological Chemistry, School of Medicine, Johns Hopkins University. Adam Ruben, ``Surviving Your Stupid, Stupid Decision to Go to Grad School,'' Broadway Books, New York, NY, 2010.
		\end{enumerate}
	\item University of British Columbia: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item UBC Faculty of Graduate Studies, {\it The Graduate Game Plan}, UBC Faculty of Graduate Studies, University of British Columbia. Available at: \url{http://www.grad.ubc.ca/current-students/gps-graduate-pathways-success/graduate-game-plan}; last accessed on August 28, 2010.
		\item UBC Faculty of Graduate Studies, {\it Resources for Achieving Success}, UBC Faculty of Graduate Studies, University of British Columbia. Available at: \url{http://www.grad.ubc.ca/current-students/gps-graduate-pathways-success/resources-achieving-success}; last accessed on August 28, 2010.
		\item UBC Faculty of Graduate Studies, {\it Research on the Lived Experience of Graduate Students}, UBC Faculty of Graduate Studies, University of British Columbia. Available at: \url{http://www.grad.ubc.ca/current-students/gps-graduate-pathways-success/research-lived-experience-graduate-students}; last accessed on August 28, 2010.
		\item UBC Faculty of Graduate Studies, {\it Resources for Graduate Student Career Development}, UBC Faculty of Graduate Studies, University of British Columbia. Available at: \url{http://www.grad.ubc.ca/current-students/gps-graduate-pathways-success/resources-graduate-student-career-development}; last accessed on August 28, 2010.
		\item UBC Faculty of Graduate Studies, {\it Graduate Guides}, UBC Faculty of Graduate Studies, University of British Columbia. Available at: \url{http://www.grad.ubc.ca/current-students/gps-graduate-pathways-success/graduate-guides}; last accessed on August 28, 2010.
		\item UBC Faculty of Graduate Studies, {\it Present and Publish Your Research}, UBC Faculty of Graduate Studies, University of British Columbia. Available at: \url{http://www.grad.ubc.ca/current-students/gps-graduate-pathways-success/present-publish-your-research}; last accessed on August 28, 2010.
		\end{enumerate}
	\item Oxford University: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item Computing Laboratory (Computer Science department): \vspace{-0.1cm}
			\begin{enumerate} \itemsep -1pt
			\item Computing Laboratory, ``D.Phil. in Computer Science,'' Oxford University. Available online at: \url{http://www.comlab.ox.ac.uk/admissions/dphil/transfer.html}; last accessed on October 29, 2010.
			\item Marta Kwiatkowska, ``How to apply for a Doctorate in the Computing Laboratory,'' Computing Laboratory, MT 2009. Available online at: \url{http://www.comlab.ox.ac.uk/admissions/dphil/howtoapply2009.pdf}; last accessed on December 17, 2010. \vspace{-0.1cm}
				\begin{itemize} \itemsep -1pt
				\item A B.S. or B.A. gives you general education; a Masters is your license to practice; and a Ph.D. is a license to teach, do research, and examine people for their Ph.D. defense.
				\item A Ph.D. ``is a research degree,'' and an ``apprentice in research''. It is ``awarded for a significant and substantial piece of research,'' and ``examined by experts and defended in a viva.''
				\item Research is about finding out about something, and discovering how to do that. It involves taking responsibility for organizing my time and taking charge of the investigation.
				\item Doing a Ph.D. is exciting as I ``carry out investigations into [the] unknown,'' and it is ``enriching to learn and master new techniques'' while doing so.
				\end{itemize}
			\end{enumerate}
		\end{enumerate}
	\item University of California, Irvine; Donald Bren School of Information and Computer Sciences: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item {\it UCI on iTunes U}, ``Improving your Grad School Application,'' University of California, Irvine: Donald Bren School of Information and Computer Sciences: Bren School Honors Seminar on November 12, 2008. Available at: \url{http://deimos3.apple.com/WebObjects/Core.woa/Browse/uci.edu.1983660442.01983660444.1975757832?i=2046363870}; last accessed on August 28, 2010. Also, see \url{http://www.oit.uci.edu/itunesu/} for {\it UCI on iTunes U}, and \url{http://www.ics.uci.edu/about/videos/index.php} for {\it Bren School iTunes U} content. [I can access this from the main {iTunes} site as follows: Look at the ``Find Educational Provider'' tab on the left panel (it's in the middle), and select ``Universities andColleges'' $\Longrightarrow$ Select ``UC Irvine'' $\Longrightarrow$ Under the Courses panel, select ``Donald Bren School of Information and Computer Sciences'' $\Longrightarrow$ Under the ``Community Outreach'' panel, select ``Improving your grad school application'' $\Longrightarrow$ watch this video. The video clip is about a panel discussion of professors about how to get into a top-tier graduate program in CS. It talks about things that admission officers look for, how to get strong letters of recommendation.]
		\end{enumerate}
	\item University of California, Davis: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item Galois Group, Department of Mathematics: \vspace{-0.1cm}
			\begin{enumerate} \itemsep -1pt
			\item University of California, Davis, {\it Useful things to know when starting graduate school... {\small ...as contributed by experienced grad students!}}, Department of Mathematics, University of California, Davis. Available at: \url{http://galois.math.ucdavis.edu/UsefulGradInfo/HelpfulAdvice/WishIdKnown}; last accessed on September 1, 2010.
			\item University of California, Davis, {\it LaTeX Tutorial}, Department of Mathematics, University of California, Davis. Available at: \url{http://galois.math.ucdavis.edu/UsefulGradInfo/GettingStarted/LaTeXTutorial}; last accessed on September 1, 2010. [ Has \LaTeX\ template for research proposal that is required for the Ph.D. qualifying exam. ]
			\item University of California, Davis, {\it Writing Your Doctoral Thesis}, Department of Mathematics, University of California, Davis. Available at: \url{http://galois.math.ucdavis.edu/UsefulGradInfo/HelpfulAdvice/WritingYourThesis}; last accessed on September 1, 2010. [ Has \LaTeX\ template for Ph.D. dissertations. ]
			\item ``If you are a UC Davis Math Grad Student, then you are a member of the Galois Group.''
			\end{enumerate}
		\end{enumerate}
	\item University of Chicago: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item Pedro F. Felzenszwalb, Department of Computer Science: \vspace{-0.2cm}
			\begin{enumerate} \itemsep -2pt
			\item \url{http://people.cs.uchicago.edu/~pff/}
			\item His paper, ``Digipaper: A Versatile Color Document Image Representation,'' has been cited 24 times in about 11 years since publication (as of September 1, 2010). He was an undergraduate then, and probably did this work as a junior or early in his senior year.
			\item His paper, ``Efficient Matching of Pictorial Structures,'' is probably based on his work done as a senior. As of September 1, 2010, this paper as been cited 222 times in about 10 years. From \url{http://cs.uchicago.edu/}, it states the following in its news section on September 1, 2010. ``Pedro Felzenszwalb receives Longuet-Higgins prize. The 2010 Longuet-Higgins award has been given to Pedro Felzenszwalb and Daniel Huttenlocher, for their paper "Efficient Matching of Pictorial Structures", Conference on Computer Vision and Pattern Recognition 2000. This award goes to a paper from 10 years ago that has made a fundamental impact on computer vision. Congratulations, Pedro!''
			\end{enumerate}
		\end{enumerate}
	\item University of Virginia: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item David Evans, {\it Advice}, Department of Computer Science, University of Virginia. Available at: \url{http://www.cs.virginia.edu/~evans/advice/}; last accessed on September 2, 2010. Also, see {\color{blue} ``advice for prospective research students''}: \url{http://www.cs.virginia.edu/~evans/advice/prospective.html}.
		\end{enumerate}
	\item University of Maryland, Baltimore County: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item Marie desJardins, Department of Computer Science and Electrical Engineering: \vspace{-0.1cm}
			\begin{enumerate} \itemsep -1pt
			\item \url{http://www.cs.umbc.edu/~mariedj/}
			\item Has information on ``How to Succeed in Graduate School,'' ``how to organize a workshop,'' and ``Presenting your research: Papers, talks and chats''.
			\item E.g., Marie desJardins, ``How to Succeed in Graduate School,'' Department of Computer Science and Electrical Engineering, University of Maryland, Baltimore County: \url{http://www.cs.umbc.edu/~mariedj/papers/advice-summary.html}
			\end{enumerate}
		\end{enumerate}
	\item University of Maryland, College Park: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item Dianne Prost O'Leary, {\it Graduate Study in the Computer and Mathematical Sciences: A Survival Guide}, Department of Computer Science, University of Maryland, College Park. Available at: \url{http://www.cs.umd.edu/~oleary/gradstudy/gradstudy.html}; last accessed on August 28, 2010. It is also available at: \url{http://www.cs.umd.edu/~oleary/gradstudy/}. See \url{http://www.cs.umd.edu/~oleary/} for more articles about ``the accessibility of computer science,'' ``8 rules for career success,'' and the disparity in gender ratios in STEM fields.
		\end{enumerate}
	\item University of Utah: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item Matt Might, {\it The illustrated guide to a Ph.D.}, School of Computing, University of Utah. Available at: \url{http://matt.might.net/articles/phd-school-in-pictures/}; last accessed on September 13, 2010. [
See {\it blog.might.net} for more articles about graduate school: \url{http://matt.might.net/articles/}; e.g., read ``10 easy ways to fail a Ph.D.'' at: \url{http://matt.might.net/articles/ways-to-fail-a-phd/}. His web page, \url{http://matt.might.net/}, has a sample of these articles. THIS IS EXCELLENT!!! ]
		\item Department of Electrical and Computer Engineering: \vspace{-0.1cm}
			\begin{enumerate} \itemsep -1pt
			\item Prof. Cynthia Furse: \vspace{-0.1cm}
				\begin{itemize} \itemsep -1pt
				\item \url{http://www.ece.utah.edu/~cfurse/}
				\item Cynthia Furse, {\it Graduate Student Survival 101}, February 2009. Available online at: \url{http://www.ece.utah.edu/~cfurse/Tutorials/UU%20Thesis/How%20to%20Write%20a%20Thesis.htm}; last accessed on December 10, 2010.
%	http://www.ece.utah.edu/~cfurse/Tutorials/UU%20Thesis/How%20to%20Write%20a%20Thesis.htm
				\item Cynthia Furse, {\it Dr. Furse's OnLine Tutorials}, August 2007. Available online at: \url{http://www.ece.utah.edu/~cfurse/Tutorials/tutorialsUofU.htm}; last accessed on December 10, 2010. [ Has a lot of good resources for teaching/lecturing, academic/technical writing (including thesis writing), advice for grad/Ph.D. students, making presentations and giving talks, writing grants and proposals, entrepreneurship, and resources for job hunting. ]
				\end{itemize}
			\end{enumerate}
		\end{enumerate}
	\item Indiana University: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item Indiana University, {\it What Every New Grad Student Should Know}, School of Informatics and Computing, Indiana University. Available at: \url{http://www.cs.indiana.edu/docproject/grad.stuff.html}; last accessed on September 1, 2010.
		\item David Chapman (Editor), {\it How to do Research At the MIT AI Lab}, AI Working Paper 316, MIT AI Lab, Massachusetts Institute of Technology, October, 1988. Available at: \url{http://www.cs.indiana.edu/docproject/grad.stuff.html}; last accessed on September 1, 2010.
		\item Marie desJardins, {\it How to Be a Good Graduate Student}, SRI International (formerly Stanford Research Institute), March 1994. Available at: \url{http://www.cs.indiana.edu/docproject/grad.stuff.html}; last accessed on September 1, 2010.
		\end{enumerate}
	\item The University of Arizona: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item Jonathan Sprinkle, {\it Students: So, you want to be my student}, Department of Electrical and Computer Engineering, The University of Arizona. Available at: \url{http://www2.engr.arizona.edu/~sprinkjm/Main/Students}; last accessed on September 5, 2010. ``Choose 2-3 IEEE or AIAA journal or conference publications from my website that interest you. Do not choose technical reports, or student papers. 
Write a critical review of the papers, including why the work is interesting, but most importantly where you think the work should go next. In this review, you are proving to me that you understand the purpose of research, and most importantly that you understand the technical details of the paper and how they relate to research.''
		\end{enumerate}
	\item Dartmouth College: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item Mark L. Tomforde, ``I've passed my quals, now what? - A guide for Ph.D. candidates in mathematics at Dartmouth College,'' Department of Mathematics, Dartmouth College, August 5, 2002. Available online at: \url{http://www.math.dartmouth.edu/graduate-students/current/guide/GradGuide.pdf}; last accessed on December 22, 2010. [ Also, available at: \url{http://www.math.dartmouth.edu/graduate-students/current/guide/} ]
		\end{enumerate}
	\item Vienna University of Technology (TU Vienna): \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item Silvia Miksch, {\it Tips: How to Do Research}, Faculty of Informatics, Vienna University of Technology. Available at: \url{http://www.ifs.tuwien.ac.at/~silvia/research-tips/}; last accessed on September 1, 2010. It has plenty of resources about: \vspace{-0.1cm}
			\begin{enumerate} \itemsep -1pt
			\item ``How to Do Research''
			\item ``How to Write a Scientific Paper''
			\item ``How to Design a Poster''
			\item ``Tips on Organizing Conferences, Workshops, and Symposia''
			\item ``How to Review''
			\item ``Digitial Libaries''
			\item ``Tips for Writing Correct English''
			\end{enumerate}
		\end{enumerate}
	\item Tufts University: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item Norman Ramsey, {\it Resources for Students}, Department of Computer Science, Tufts University. Available at: \url{http://www.cs.tufts.edu/~nr/students/}; last accessed on September 2, 2010.
		\item Norman Ramsey, {\it How to get admitted to a PhD program}, Department of Computer Science, Tufts University. Available at: \url{http://www.cs.tufts.edu/~nr/students/admit.html}; last accessed on September 2, 2010.
		\end{enumerate}
	\item Portland State University: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item Department of Computer Science; Maseeh College of Engineering and Computer Science: \vspace{-0.1cm}
			\begin{enumerate} \itemsep -1pt
			\item PSU CS 569 (MS Students) and CS 669 (PhD students) - Scholarship Skills (Fall 2010) by Prof. Andrew Black and Tim Sheard. Available online at: \url{http://web.cecs.pdx.edu/~black/ScholarshipSkills/}; last accessed on September 29, 2010.
			\end{enumerate}
		\end{enumerate}
	\item State University of New York at Buffalo: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item William J. Rapaport, {\it Information for Grad Students in Computer Science \& Engineering at UB}, Department of Computer Science and Engineering, Department of Philosophy, and Center for Cognitive Science, State University of New York at Buffalo, Buffalo, NY. Available at: \url{http://www.cse.buffalo.edu/~rapaport/GRAD/}; last accessed on September 2, 2010.
		\end{enumerate}
	\item The Ohio State University: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item The Ohio Science and Engineering Alliance: \vspace{-0.1cm}
			\begin{enumerate} \itemsep -1pt
			\item Graduate School: \url{http://www.ohiosea.org/academic/academic_grad.html}
			\end{enumerate}
		\end{enumerate}
	\item Swarthmore College: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item Department of History: \vspace{-0.1cm}
			\begin{enumerate} \itemsep -1pt
			\item Timothy Burke, ``Should You Go to Graduate School?,'' in his blog {\it Easily Distracted: Culture, Politics, Academia and Other Shiny Objects}, Department of History, Swarthmore College. Available at: \url{http://weblogs.swarthmore.edu/burke/permanent-features-advice-on-academia/features/}; last accessed on September 14, 2010. [ Also, see \url{http://www.swarthmore.edu/SocSci/tburke1/gradschool.html}. ]
			\item Timothy Burke, ``From ABD to the Job Market: Advice for the Grad School Endgame,'' in his blog {\it Easily Distracted: Culture, Politics, Academia and Other Shiny Objects}, Department of History, Swarthmore College. Available at: \url{http://weblogs.swarthmore.edu/burke/permanent-features-advice-on-academia/abd/}; last accessed on September 14, 2010.
			\end{enumerate}
		\end{enumerate}
	\item Georgetown University: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item Department of Economics: \vspace{-0.1cm}
			\begin{enumerate} \itemsep -1pt
			\item Garance Genicot, ``Applying to Grad School in Economics,'' Department of Economics, Georgetown University. Available online at: \url{http://www9.georgetown.edu/faculty/gg58/GradSchool.html}; last accessed on January 9, 2010.
			\end{enumerate}
		\end{enumerate}
	\item Norwegian University of Science and Technology: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item ``PhD Studies,'' Department of Computer and Information Science; Faculty of Information Technology, Mathematics and Electrical Engineering. Available online at: \url{http://www.idi.ntnu.no/research/phd.php}; last accessed on September 29, 2010. [ Includes an outline of a Ph.D. research proposal that is required for applications to its Ph.D. program in computer science. ]
		\end{enumerate}
	\item North Carolina State University: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item Richard M. Felder, ``An Engineering Student Survival Guide,'' Department of Chemical and Biomolecular Engineering, North Carolina State University, 1993. Available at: \url{http://www4.ncsu.edu/unity/lockers/users/f/felder/public/Papers/survivalguide.htm}; last accessed on August 27, 2010.
		\item Matthias F. (Matt) Stallmann, ``What CSC Graduates Should Know,'' Department of Computer Science, North Carolina State University, February 9, 1996. Available online at: \url{http://people.engr.ncsu.edu/mfms/Teaching/what-grads-should-know.html}; last accessed on October 6, 2010.
		\end{enumerate}
	\item Michigan State University: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item The Graduate School: \vspace{-0.1cm}
			\begin{enumerate} \itemsep -1pt
			\item The Graduate School, {\it ``Setting Expectations and Resolving Conflict'' Program: Developing Communication and Conflict Management Skills to Save Time and Enhance Productivity}, The Graduate School, Michigan State University, July 12, 2010. Available online at: \url{http://grad.msu.edu/conflictresolution/}; last accessed on December 22, 2010.
			\end{enumerate}
		\item Collegiate Employment Research Institute: \vspace{-0.1cm}
			\begin{enumerate} \itemsep -1pt
			\item \url{http://www.ceri.msu.edu/}
			\item Recruiting Trends 2010-2011: \url{http://www.ceri.msu.edu/recruiting-trends-2009-2010/}
			\end{enumerate}
		\end{enumerate}
	\item San Francisco State University: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item Eric Hsu, Department of Mathematics: \vspace{-0.1cm}
			\begin{enumerate} \itemsep -1pt
			\item Eric Hsu, {\it Math Education Job Search Resources}, Department of Mathematics, San Francisco State University. Available at: \url{http://bfc.sfsu.edu/cgi-bin/hsu.pl?Math_Education_Job_Search_Resources}; last accessed on September 1, 2010. Also, accessible at: \url{http://math.sfsu.edu/hsu/jobs.html}.
			\item Has lots of information on applying for positions in academia.
			\item Has lists of postdoc positions and (junior) faculty openings.
			\end{enumerate}
		\end{enumerate}
	\item Colorado School of Mines: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item Department of Physics: \vspace{-0.1cm}
			\begin{enumerate} \itemsep -1pt
			\item Robert L. Read, ``How to be a Programmer,'' APPLICATI, 2003. Available online at: \url{http://samizdat.mines.edu/howto/}; last accessed on September 28, 2010. [ Another publisher is FEINHOCHBURG ]
			\end{enumerate}
		\end{enumerate}
	\item New Mexico Institute of Mining and Technology (New Mexico Tech): \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item Brian Borchers, ``Recommendation Letters,'' Department of Mathematics, New Mexico Institute of Mining and Technology. Available at: \url{http://infohost.nmt.edu/~borchers/recletters.html}; last accessed on September 2, 2010.
		\end{enumerate}
	\item University of Minnesota Duluth: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item University of Minnesota Duluth, {\it Is Graduate School Right For You?}, Career Services, University of Minnesota Duluth. Available at: \url{http://www.d.umn.edu/careers/grad_school/right_for_you.html}; last accessed on September 2, 2010.
		\end{enumerate}
	\item The University of Waikato: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item Sean Oughton, {\it Graduate School Survival Guide}, Department of Mathematics, The University of Waikato. Available at: \url{http://www.math.waikato.ac.nz/~seano/grad-school-advice.html}; last accessed on September 3, 2010. [ Also, see \url{http://www.math.waikato.ac.nz/~seano/} for Sean's web page. ]
		\end{enumerate}
	\item Institute for Operations Research and the Management Sciences (INFORMS): \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item {\it Career Center} (has some information on funding/fellowships, and academic careers): \url{http://www.informs.org/Build-Your-Career/INFORMS-Student-Union/Career-Center}
		\end{enumerate}
	\item The PhD Project: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item Resources for Potential/Current Doctoral Students: \vspace{-0.1cm}
			\begin{enumerate} \itemsep -1pt
			\item \url{http://www.phdproject.org/resources.html}
			\item Information about good business schools that offer Ph.D. programs, preparation for the GMAT, and the life in graduate school as a Ph.D. student.
			\item Suggested Reading: \vspace{-0.1cm}
				\begin{itemize} \itemsep -1pt
				\item \url{http://www.phdproject.org/reading.html}
				\item Has information life in graduate school as a Ph.D. student, racial diversity/issues in higher education, job searching in academia, and work-life balance for female Ph.D. students.
				\end{itemize}
			\end{enumerate}
		\end{enumerate}
	\item U.S. Department of Education: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item National Center for Education Statistics (NCES); Institute of Education Sciences: \vspace{-0.1cm}
			\begin{enumerate} \itemsep -1pt
			\item National Center for Education Statistics, {\it Projections of Education Statistics to 2018} [report], National Center for Education Statistics, Institute of Education Sciences, U.S. Department of Education, September 2009. Available online at: \url{http://nces.ed.gov/programs/projections/projections2018/index.asp}; last accessed on January 7, 2010.
			\end{enumerate}
		\end{enumerate}
	\item ABD Solution Company: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item Dr. Carters Educational Group, L.L.C.: \vspace{-0.1cm}
			\begin{enumerate} \itemsep -1pt
			\item Wendy Y. Carter, {\it TA-DA!}\texttrademark\ {\it Thesis and Dissertation Accomplished}, 2011. Available online at: \url{http://www.tadafinallyfinished.com/index.html}; last accessed on January 8, 2010. \vspace{-0.1cm}
				\begin{itemize} \itemsep -1pt
				\item {\it TA-DA!}\texttrademark\ Links and Resources: \url{http://www.tadafinallyfinished.com/links/index.html}
				\end{itemize}
			\item Educational Research Institute: \vspace{-0.1cm}
				\begin{itemize} \itemsep -1pt
				\item \url{http://www.educationalresearchinstitute.org/}
				\end{itemize}
			\end{enumerate}
		\end{enumerate}
	\item About.com: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item About.com, {\it Graduate School}. Available at: \url{http://gradschool.about.com/}; last accessed on August 25, 2010.
		\item Timothy Dzurilla, {\it Writing Graduate Application Essay: Tips to Writing a Successful Personal Statement}, About.com, Nov 1, 2007. Available at: \url{http://www.suite101.com/content/writing-graduate-application-essay-a34598}; last accessed on September 1, 2010. [ Help with writing a statement of purpose ]
		\item Naomi Rockler-Gladen, {\it How to Choose a Graduate School: Faculty, Fit, Student Culture, and Other Grad Program Considerations}, About.com, Nov 12, 2007. Available at: \url{http://www.suite101.com/content/how-to-choose-a-graduate-school-a35387}; last accessed on September 1, 2010. [ How to select a graduate program ... EXCELLENT ]
		\item Naomi Rockler-Gladen, {\it How to Choose a Graduate Advisor: Finding a Faculty Member to Direct an MA Thesis or PhD Dissertation}, About.com, Oct 30, 2007. Available at: \url{http://www.suite101.com/content/how-to-choose-a-graduate-advisor-a34468}; last accessed on September 1, 2010. [ How to pick an advisor ... EXCELLENT ]
		\end{enumerate}
	\item UndergradEcon.com, {\it Graduate School Economics}. Available online at: \url{http://www.undergradecon.com/grad_school.html}; last accessed on January 9, 2010.
	\item Sumit Gupta, {\it Articles and Information about Graduate School}. Available at: \url{http://www.4bearsonline.com/collections/grad/index.shtml}; last accessed on August 25, 2010. 
	\item William Stallings: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item {\it Computer Science Student Resource Site: How-To}: \url{http://www.computersciencestudent.com/SS/SS-howto.html}
		\item {\it Computer Science Student Resource Site: Computer Science Careers}: \url{http://www.computersciencestudent.com/SS/SS-career.html}
		\item {\it Computer Science Student Resource Site}: \url{http://www.computersciencestudent.com/}
		\end{enumerate}
	\item Dario Toncich, {\it Key Factors in Postgraduate Research - A Guide for Students}. Available at: \url{http://www.doctortee.net/KeyFactors.html}; last accessed on September 1, 2010.
	\end{enumerate}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\item Grad school admission advice: \vspace{-0.3cm}
	\begin{enumerate} \itemsep -2pt
	\item University of California, Berkeley: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item Department of Economics, ``Criteria,'' Department of Economics, University of California, Berkeley. Available at: \url{http://www.econ.berkeley.edu/econ/grad/admit-criteria.shtml}; last accessed on August 28, 2010.
		\end{enumerate}
	\item Harvard University: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item Susan Athey, ``Advice for Applying to Grad School in Economics,'' Department of Economics, Harvard University. Available at: \url{http://kuznets.fas.harvard.edu/~athey/gradadv.html}; last accessed on August 28, 2010.
		\end{enumerate}
	\item Statementofpurpose.com: \url{http://www.statementofpurpose.com/}
	\end{enumerate}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\item Advice concerning research: \vspace{-0.3cm}
	\begin{enumerate} \itemsep -2pt
	\item University of California, Riverside: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item John Baez, ``Advice for the Young Scientist,'' Department of Mathematics, University of California, Riverside, March 25, 2007. Available at: \url{http://math.ucr.edu/home/baez/advice.html}; last accessed on August 28, 2010.
		\end{enumerate}
	\item Research Information Network, RIN: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item Researchers resources: \url{http://www.rin.ac.uk/resources/researcher-resources}
		\item Researcher development and skills: \url{http://www.rin.ac.uk/resources/researcher-development-and-skills}
		\item Publishing: \url{http://www.rin.ac.uk/resources/publishing}
		\item Learned and professional society: \url{http://www.rin.ac.uk/resources/learned-and-professional-society}
		\end{enumerate}
	\end{enumerate}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\item advice about giving presentations: \vspace{-0.3cm}
	\begin{enumerate} \itemsep -2pt
	\item Cornell University, Department of Computer Science, Faculty of Computing and Information Science (CIS): \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item Charles F. Van Loan, ``The Short Talk,'' Department of Computer Science, Cornell University. Available at: \url{http://www.cs.cornell.edu/cv/ShortTalk.htm}; last accessed on August 25, 2010.
		\end{enumerate}
	\item University of Wisconsin-Madison, Computer Sciences Department: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item Mark D. Hill, ``Oral Presentation Advice,'' Computer Sciences Department, University of Wisconsin-Madison, April 1992, Revised January 1997. Available at: \url{http://pages.cs.wisc.edu/~markhill/conference-talk.html}; last accessed on August 25, 2010. It includes a short summary of a presentation on this topic by Prof. David A. Patterson. David A. Patterson, ``How to Give a Bad Talk,'' Computer Science Division, Department of Electrical Engineering and Computer Sciences, University of California-Berkeley, 1983.
		\end{enumerate}
	\item University of California, Los Angeles: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item Terence Tao, ``Talks are not the same as papers,'' Department of Mathematics, University of California, Los Angeles. Available at: \url{http://terrytao.wordpress.com/career-advice/talks-are-not-the-same-as-papers/}; last accessed on September 1, 2010.
		\end{enumerate}
	\item North Carolina State University, Department of Chemical and Biomolecular Engineering: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item Richard M. Felder, ``Tips on Talks,'' Department of Chemical and Biomolecular Engineering, North Carolina State University. Available at: \url{http://www4.ncsu.edu/unity/lockers/users/f/felder/public/Papers/speakingtips.htm}; last accessed on August 28, 2010.
		\end{enumerate}
	\item Random information: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item The number of presentation slides is approximately the same as the number of minutes allocated for the presentation. Therefore, for a 15 minutes presentation, the speaker shall use about 15 slides for her/his presentation.
		\item 
		\end{enumerate}
	\end{enumerate}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\item Advice on studying: \vspace{-0.3cm}
	\begin{enumerate} \itemsep -2pt
	\item State University of New York at Buffalo, Department of Computer Science and Engineering: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item William J. Rapaport, ``How to Study: A Brief Guide,'' Department of Computer Science and Engineering, Department of Philosophy, and Center for Cognitive Science, State University of New York at Buffalo, Buffalo, NY. Available at: \url{http://www.cse.buffalo.edu/~rapaport/howtostudy.html}; last accessed on August 25, 2010.
		\end{enumerate}
	\item University of Oregon, Teaching and Learning Center: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item Ronald C. Blue, ``How to Study,'' Teaching and Learning Center, University of Oregon. Available at: \url{http://tep.uoregon.edu/resources/faqs/outsidehelp/study.html}; last accessed on August 25, 2010.
		\end{enumerate}
	\item North Carolina State University, Department of Chemical and Biomolecular Engineering: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item Richard M. Felder, ``Handouts for Students,'' Department of Chemical and Biomolecular Engineering, North Carolina State University. Available at: \url{http://www4.ncsu.edu/unity/lockers/users/f/felder/public/Student_handouts.html}; last accessed on August 28, 2010.
		\end{enumerate}
	\item Middle Tennessee State University: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item Carolyn Hopper, ``The Study Skills Help Page: Learning Strategies for Success,'' Middle Tennessee State University. Available at: \url{http://frank.mtsu.edu/~studskl/}; last accessed on August 25, 2010.
		\end{enumerate}
	\item Joseph Frank Landsberger: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item Joseph Frank Landsberger, {\it Study Guides and Strategies}. Available at: \url{http://www.studygs.net/}; last accessed on August 25, 2010.
		\end{enumerate}
	\end{enumerate}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\item Advice on test preparation and test taking: \vspace{-0.3cm}
	\begin{enumerate} \itemsep -2pt
	\item North Carolina State University: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item Richard M. Felder, ``Random Thoughts:  Memo,'' {\it Chemical Engineering Education}, Vol. 33, No. 2, pp. 136--137, 1999. Available at: \url{http://www4.ncsu.edu/unity/lockers/users/f/felder/public/Columns/memo.html}; last accessed on August 28, 2010.
		\item Richard M. Felder and James E. Stice, ``Tips on Test Taking,'' Department of Chemical and Biomolecular Engineering, North Carolina State University, and Deptartment of Chemical Engineering, The University of Texas at Austin. Available at: \url{http://www4.ncsu.edu/unity/lockers/users/f/felder/public/Papers/testtaking.htm}; last accessed on August 28, 2010.
		\item Richard M. Felder and Matthias F. (Matt) Stallmann, ``Tips for Test Takers,'' Department of Computer Science, North Carolina State University, February 17, 2005. Available online at: \url{http://people.engr.ncsu.edu/mfms/Teaching/tips-for-test-takers.html}; last accessed on October 6, 2010.
		\end{enumerate}
	\end{enumerate}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\item Advice for engineering students: \vspace{-0.3cm}
	\begin{enumerate} \itemsep -2pt
	\item University of Maryland, Baltimore County; Department of Computer Science and Electrical Engineering: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item Alan T. Sherman (Alan Theodore Sherman), {\it How To's and Other Generic Course Documents}, Department of Computer Science and Electrical Engineering, University of Maryland, Baltimore County, September 12, 1995. Available at: \url{http://www.csee.umbc.edu/~sherman/Courses/documents/}; last accessed on August 28, 2010. Also, see \url{http://www.csee.umbc.edu/~sherman/Courses/}.
		\item Alan T. Sherman (Alan Theodore Sherman), {\it Teaching Activites}, Department of Computer Science and Electrical Engineering, University of Maryland, Baltimore County. Available at: \url{http://www.csee.umbc.edu/~sherman/mycourses.html}; last accessed on August 28, 2010.
		\end{enumerate}
	\item North Carolina State University, Department of Chemical and Biomolecular Engineering: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item Richard M. Felder's column, ``Random Thoughts,'' in the journal, {\it Chemical Engineering Education}. Available at: \url{http://www4.ncsu.edu/unity/lockers/users/f/felder/public/Columns.html}; last accessed on August 28, 2010.
		\item Richard M. Felder, ``An Engineering Student Survival Guide,'' Department of Chemical and Biomolecular Engineering, North Carolina State University, 1993. Available at: \url{http://www4.ncsu.edu/unity/lockers/users/f/felder/public/Papers/survivalguide.htm}; last accessed on August 27, 2010. \vspace{-0.2cm}
			\begin{itemize} \itemsep -2pt
			\item Do not expect people to tell me how to solve certain problems, especially implementation details as a researcher.
			\item Learn to find out for myself what I need to know. That is, determine the scope of things that I need to know, the time frame and deadline(s) in which I should acquire knowledge of those skills and knowledge, and create a plan to acquire those skills and knowledge.
			\item I should learn to be more resourceful, and determine where can I get help. Particularly, resources (e.g., publications and online material), individuals, and networks of people that can provide a significant amount of help to people.
			\item Make a serious effort to solve a problem before I approach others for help. Else, they may get annoyed when I did not bother to learn how to solve problems that are actually very simple. Also, bring my (attempted/considered) solutions to the people who I seek help from. Show them my flow charts, schematics, calculations, algorithms, and heuristics. This would convince them that I have done my homework, and am not asking bane questions.
			\item To help me understand how to apply the skills and knowledge that I am acquiring in ``practical, real-world applications,'' I should look at textbooks (including alternative textbooks/books, such as handbooks and encyclopedias) for such examples. I can also look ahead further in the chapter, book, or books of subsequent classes to see how these skills and knowledge will be applied. Note that information that I skip while reading my textbook, manuals, and guides may actually contain the solution that I am looking for. Think of the questions that I asked Anders Franzen about the SMT-LIB manual during my internship at FBK while working on the {\it MathSAT} project. I did not understand the material in the manual, since I lacked a background in compiler design and formal grammar/languages. So, I had to get he to help me interpret what I was reading. This was like when I was learning about UNIX as a freshman/sophomore. I did not understand what I was reading when I looked at the UNIX manual (``man pages''). Thus, I shall learn how to read technical literature better.
			\item By reading technical and semi-technical magazines and newspapers/newsletters, I can learn about ``practical, real-world applications'' of the things that I am learning about. In addition, by talking to others (students further ahead of me in engineering education and professional engineers), I learn to see how can I apply the things that I am learning about in ``practical, real-world applications''. Furthermore, I can tap into the newsletters and technical magazines of professional organizations, such as ACM and IEEE, to find out about research opportunities/projects where I can apply what I am learning about.
			\item If my lecture slides/notes and textbooks(s) do not have adequate worked-out examples (e.g., only trivial examples) to help me understand mathematical theories and formulas, and engineering concepts, I shall seek other resources. E.g., I can look at lecture slides/notes from equivalent/similar classes that are taught at other universities. In addition, I can look at other textbooks/books on this subject. Note that for advanced topics, such as those covered by advanced graduate classes, I may only be able to find 1 or 2 books on this topic. So, I may not always have the luxury of looking at worked examples from other textbooks; e.g., I could find many textbooks for differential equations and vector analysis, but not for antenna analysis or satisfiability modulo theories.
			\item I shall improve my ability to work out problems on my own if I cannot find adequate examples for that problem or similar problems. In addition, I shall document worked solutions digitally, so that I can refer to them during revision for an exam, my prelims/quals, or when I encounter a similar problem during research and development.
			\item I shall also improve the way I revise/relearn concepts, technologies, skills, and knowledge. Documenting resources and prior solutions to problems would help me relearn things. Such documentation requires proper information management, so that I can reuse the previously acquired knowledge and skills. Remember that using \LaTeX\ on a UNIX-like operating system helps me with information management.
			\item If I do not understand how and why things work, determine if knowledge of that is required for solving problems in my research/class project, or assignment. If not, I can move on and address this when I have more free time (e.g., ``slack'' periods during the calendar year). To find out more about how certain things work, I can look into the references in my lecture slides/notes and textbooks(s), or search/google for references online. Note that learning how and why certain things work may require (advanced) knowledge that is outside the scope of my discipline or research area. Hence, it is important to know when to stop delving into (/investigating/probing) a concept/technique. Remember my problems with understanding Prof. Sanjit A. Seshias publications on adaptive eager encodings, in which he used ``polyhedral theory'' (I believe in the context of integer programming and combinatorial optimization) to prove a theorem regarding the satisfiability of UTVPI formulas? Ditto for lambda expressions (and lambda calculus) so that I can understand how syntax is represented for
	a given signature in first-order logic.]
			\item I shall improve my ability to convert descriptions of architectures and techniques into hardware/software implementations. It is easier to grasp the concepts in pseudocode, flowcharts, schematics, figures, and demonstrations than to learn the concepts from text and create abstractions of those concepts on my own. I shall improve my ability to create pseudocode, flowcharts, schematics, figures, and demonstrations from what I have read, especially in journal and conference papers.
			\item I shall improve my ability to perform statistical analysis on my experimental data, and analyze the figures/graphs that I have plotted.
			\item Use a book from the {\it Schaum's Outline} series from {\it McGraw-Hill} to help me learn material from introductory and intermediate classes. ``Even if you can't find a reference with exactly the type of coverage that works best for you, just reading about the same topic in two different places usually clarifies the ideas.'' [Remember how I read about the same topic in different advance engineering math textbooks to learn concepts for my classes in differential equations and vector analysis?]
			\item Working with others allows me to overcome obstacles that I may not be able to overcome on my own. While I may give up on learning certain things or overcome specific problems in individual projects, my teammates may be able to come up with solutions to problems in group projects. In addition, working in a diverse group exposes me to solutions that can be more effective and/or efficient... {\it students routinely teach one another in group work -- and as any professor will tell you, teaching something is probably the most effective way to learn it.}
			\item Try to find groups of three to four people to work on a problem. When I work in pairs, I may not expose myself to a sufficient variety of approaches. Similarly, when I work in larger groups (i.e., $> 4$), some individuals may be left out of the ``active problem-solving process''.
			\item I shall endeavor to outline solution on my own first, without being boggled or encumbered by the implementation details. Subsequently, I can work out the complete solutions with my group. If each individual does this, each group member can learn how to get started in solving problems in the project. That is, let's outline solutions to the problem, before we meet to discuss our considered solutions and develop the complete solution together.
			\item ``For group work to be fully effective, every group member should be able to explain in detail every solution obtained in a work session. Having the group members (particularly the weaker ones) go through these explanations before ending the session is a good way to make sure that the session has achieved its objectives.'' This will mitigate the tendency for the more technically challenged and reserved individuals to accept proposed solutions without understanding those solutions.
			\end{itemize}
		\item Richard M. Felder, ``How to Survive Engineering School,'' Department of Chemical and Biomolecular Engineering, North Carolina State University. Available at: \url{http://www4.ncsu.edu/unity/lockers/users/f/felder/public/Columns/Surviving-School.html}; last accessed on August 28, 2010.
		\end{enumerate}
	\end{enumerate}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\item Advice on teaching: \vspace{-0.3cm}
	\begin{enumerate} \itemsep -2pt
	\item Stanford University: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item Stanford University, {\it Teaching at Stanford}, Center for Teaching and Learning, Stanford University. Available at: \url{http://ctl.stanford.edu/teaching-at-stanford.html}; last accessed on September 1, 2010.
		\item Stanford University, {\it Handouts and Teaching Tips}, Center for Teaching and Learning, Stanford University. Available at: \url{http://ctl.stanford.edu/teachingta/handouts-and-teaching-tips.html}; last accessed on September 1, 2010.
		\item Stanford University, {\it Speaking of Teaching Newsletters}, Center for Teaching and Learning, Stanford University. Available at: \url{http://ctl.stanford.edu/speaking-of-teaching-newsletters.html}; last accessed on September 1, 2010.
		\end{enumerate}
	\item University of California, Riverside; Department of Mathematics: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item John Baez, ``How to Teach Stuff,'' Department of Mathematics, University of California, Riverside, January 23, 2006. Available at: \url{http://math.ucr.edu/home/baez/teaching.html}; last accessed on August 28, 2010.
		\end{enumerate}
	\item University of Oregon, Teaching and Learning Center: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item Teaching Effectiveness Program, {\it Teaching Resources}, Teaching and Learning Center, University of Oregon. Available at: \url{http://tep.uoregon.edu/resources/index.html}; last accessed on August 25, 2010. Also, look the ``Teaching FAQ's'': \url{http://tep.uoregon.edu/resources/faqs/}
		\item Teaching Effectiveness Program, Resources for {\it Teaching with Technology}, Teaching and Learning Center, University of Oregon. Available at: \url{http://tep.uoregon.edu/technology/index.html}; last accessed on August 25, 2010.
		\end{enumerate}
	\item North Carolina State University, Department of Chemical and Biomolecular Engineering: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item Richard M. Felder, {\it Student-centered Teaching and Learning}, Department of Chemical and Biomolecular Engineering, North Carolina State University. Available at: \url{http://www4.ncsu.edu/unity/lockers/users/f/felder/public/Student-Centered.html}; last accessed on August 28, 2010.
		\item Richard M. Felder, {\it Index of Learning Styles}, Department of Chemical and Biomolecular Engineering, North Carolina State University. Available at: \url{http://www4.ncsu.edu/unity/lockers/users/f/felder/public/ILSpage.html}; last accessed on August 28, 2010.
		\item Richard M. Felder, {\it Learning Styles}, Department of Chemical and Biomolecular Engineering, North Carolina State University. Available at: \url{http://www4.ncsu.edu/unity/lockers/users/f/felder/public/Learning_Styles.html}; last accessed on August 28, 2010.
		\item Richard M. Felder, {\it Richard Felder's Education-related Publications}, Department of Chemical and Biomolecular Engineering, North Carolina State University. Available at: \url{http://www4.ncsu.edu/unity/lockers/users/f/felder/public/Papers/Education_Papers.html}; last accessed on August 28, 2010.
		\end{enumerate}
	\item Joseph Frank Landsberger: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item Joseph Frank Landsberger, {\it Teaching Guides and Strategies}. Available at: \url{http://www.studygs.net/teaching/}; last accessed on August 25, 2010.
		\end{enumerate}
	\end{enumerate}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\item Resources to improve my English skills: \vspace{-0.3cm}
	\begin{enumerate} \itemsep -2pt
	\item {\it Guide to Online Schools}: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item {\it Guide to Online Schools} [or {\it GuideToOnlineSchools.com}], {\it Resources to Help Improve Your English Pronunciation}. Available at: \url{http://www.guidetoonlineschools.com/tips-and-tools/english-pronunciation}; last accessed on August 25, 2010.
		\end{enumerate}
	\end{enumerate}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\item time management: \vspace{-0.3cm}
	\begin{enumerate} \itemsep -2pt
	\item {\it Guide to Online Schools}: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item {\it Guide to Online Schools} [or {\it GuideToOnlineSchools.com}], {\it The Best Compilation of Time Management Resources on the Web}. Available at: \url{http://www.guidetoonlineschools.com/tips-and-tools/time-management}; last accessed on August 25, 2010.
		\end{enumerate}
	\end{enumerate}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\item Math and Science revision: \vspace{-0.3cm}
	\begin{enumerate} \itemsep -2pt
	\item Basic high school math: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item North Carolina State University, Department of Chemical and Biomolecular Engineering: \vspace{-0.1cm}
			\begin{itemize} \itemsep -1pt
			\item Kenny Felder and Gary Felder, ``Kenny's Math and Physics Help,'' 2009. Available at: \url{http://www4.ncsu.edu/unity/lockers/users/f/felder/public/kenny/home.html}; last accessed on August 28, 2010.
			\item Kenny Felder, ``Selected Other Educational Sites on the Web''. Available at: \url{http://www4.ncsu.edu/unity/lockers/users/f/felder/public/kenny/edulinks.html}; last accessed on August 28, 2010.
			\end{itemize}
		\end{enumerate}
	\end{enumerate}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\item good blogs about graduate school: \vspace{-0.3cm}
	\begin{enumerate} \itemsep -2pt
	\item Marc Eaddy, {\it Marc Eaddy: Confessions of an Ex-PhD Student}. Available at: \url{http://marceaddy.blogspot.com/}; last accessed on August 28, 2010.
	\item The Academic Blog Portal: \url{http://academicblogs.org/wiki/index.php/Main_Page}
	\end{enumerate}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\item fun stuff about grad school: \vspace{-0.3cm}
	\begin{enumerate} \itemsep -2pt
	\item Jorge Cham, {\it Piled Higher and Deeper}. Available at: \url{http://www.phdcomics.com/}; last accessed on August 28, 2010. See the latest ``PHD Comics'' at: \url{http://www.phdcomics.com/comics.php}. This comic strip pokes fun at the [fun, harsh, interesting, and absurd] realities of life in grad school.
	\item Jorge Cham, {\it Academica}. Available online at: \url{http://academia.edu/academica}; last accessed on October 3, 2010.
	\item Jorge Cham, {\it The PhD Forums}. Available online at: \url{http://www.phdcomics.com/proceedings/index.php}; last accessed on October 3, 2010. [ Has useful guidelines for surviving graduate school and is a decent resource for some technical support (e.g., with \LaTeX\ or C++). ]
	\end{enumerate}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\item other information about or related to grad school (and higher education): \vspace{-0.3cm}
	\begin{enumerate} \itemsep -2pt
	\item {\it Eurodoc}: union of grad student associations of each European country; see \url{http://en.wikipedia.org/wiki/EURODOC} and \url{http://www.eurodoc.net/}
	\item {\it European Association for Quality Assurance in Higher Education} (ENQA): union of accreditation board(s) of each European country; see \url{http://en.wikipedia.org/wiki/ENQA} and \url{http://www.enqa.eu/}
	\item {\it Innolyst}: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item Innolyst, {\it ResearchCrossroads}, Innolyst: \vspace{-0.1cm}
			\begin{enumerate} \itemsep -1pt
			\item Ernest Kuh, UC Berkeley: \url{http://www.researchcrossroads.org/Researchers/830167} or \url{http://www.researchcrossroads.org/index.php?option=com_content&view=article&id=49&Itemid=55&user_id=830167}
			\item US-based researchers who receive US government funding for their research have profiles in {\it ResearchCrossroads}. E.g., I can find the amount of public funding that my professors at USC received, and the organization that funds them. I can also read an abstract of the project that they got funded for.
			\item \url{http://www.researchcrossroads.org/}
			\end{enumerate}
		\item \url{http://www.innolyst.com/}
		\end{enumerate}
	\item A. Lee, C. Dennis, and P. Campbell. Nature's guide for mentors. Nature, 447(7146):791--797, June 14, 2007 \cite{Lee2007}.
	\item American Council of Trustees and Alumni (ACTA): \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item The American Council of Trustees and Alumni (ACTA) is an independent, non-profit organization committed to academic freedom, excellence, and accountability at Americas colleges and universities.
		\item Launched in 1995, we are the only organization that works with alumni, donors, trustees, and education leaders across the United States to support liberal arts education, uphold high academic standards, safeguard the free exchange of ideas on campus, and ensure that the next generation receives a philosophically rich, high-quality college education at an affordable price.
		\item ACTA Publications: \url{https://www.goacta.org/publications/}. [ ACTA publications cover many aspects of issues concerning higher education institutions, and serve to provide standards of academic excellence and strategies for achieving these standards. ]
		\end{enumerate}
		\item GOOD, {\it GOOD Education}: \url{http://www.good.is/series/good-education/}
	\item Lumina Foundation for Education, {\it Publications}. Available at: \url{http://www.luminafoundation.org/publications/}; last accessed on September 4, 2010.
	\item National Center for Academic Transformation: \url{http://thencat.org/}
	\item Graduate Software Engineering 2009 (GSwE2009): \url{http://www.gswe2009.org/}
	\item CollegeMeasures.org (a joint endeavor by American Institutes for Research and Matrix Knowledge Group): \url{http://collegemeasures.org/}
	\item Association of American Colleges and Universities (AAC\&U): \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item \url{http://www.aacu.org/}
		\item DiversityWeb: \vspace{-0.1cm}
			\begin{enumerate} \itemsep -1pt
			\item The DiversityWeb project is housed within the Office of Diversity, Equity and Global Initiatives at the Association of American Colleges and Universities (AAC\&U)
			\item \url{http://www.diversityweb.org/index.cfm}
			\end{enumerate}
		\end{enumerate}
	\item Newsweek Education: \url{http://education.newsweek.com/index.html}
	\item GRE: \cite{Green2000,Stewart2003,Kaplan2008,ETS2007,Wells2005,Lurie2002,Wu2007,Curtis2007}
	\item Council for Higher Education Accreditation: \url{http://www.chea.org/}
	\item Council of Graduate Schools (CGS): \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item \url{http://www.cgsnet.org/}
		\item Ph.D. Completion Project: \url{http://www.phdcompletion.org/}
		\end{enumerate}
	\item Unigo: \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item \url{http://www.unigo.com/}
		\item Offers students' perspectives on various aspects of college life, from admissions and dorm/college life to studying abroad and academics (studying skills and selecting a major)
		\end{enumerate}
	\item NAFSA / Association of International Educators (formerly, National Association of Foreign Student Advisers): \vspace{-0.2cm}
		\begin{enumerate} \itemsep -2pt
		\item \url{http://www.nafsa.org/}
		\item For Students: \vspace{-0.1cm}
			\begin{enumerate} \itemsep -1pt
			\item \url{http://www.nafsa.org/students.sec/}
			\item Resources about seeking financial aid for study abroad programs, absentee ballot procedure
			\end{enumerate}
		\item {\it Connecting Our World}: \url{http://www.connectingourworld.org/}
		\end{enumerate}
	\end{enumerate}
\end{itemize}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\subsubsection{\hspace{0.1in} Zhiyang's Suggestions for Graduate School Applications}
%\label{zygradschapps}
\input{grad_school_apps_copy}







%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Thoughts and Resources for Specific Areas and Topics
%	\input{./have2innovate/outreach}


%	http://www1.ccny.cuny.edu/advancement/news/Location-Determines-Social-Network-Influence.cfm
%	http://www.computerworld.com/s/article/9182138/MIT_builds_swimming_oil_eating_robots
%	http://creativecommons.org/licenses/by-sa/3.0/us/

{\linespread{1}
%\bibliographystyle{IEEEtran}
\bibliographystyle{plain}
%\bibliography{./others/references}
%\bibliography{/data/others/notes/references}
%\bibliography{/data/research/zhiyang_references/references}
\bibliography{/Users/zhiyang/Documents/ricerca/lassi-bibtex/references}

\addcontentsline{toc}{section}{Bibliography}
}

























%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{document}